---
title: "Mouse-all-controls-LR-split"
author: "Elisa Guma"
date: "4/12/2022"
output: html_document
---
#Description
In this script we calculate group differences between XXY and XYY males relative to XY males.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries
```{r }
library(tidyverse)
library(data.tree)
library(RMINC)
library(magrittr)
library(ggplot2)
library(MRIcrotome)
library(ggpubr)
library(raincloudplots)
library(cowplot)
library(readr)
library(PupillometryR)
library(colortools)
```

# Load in data
```{r}
pathHome <- "/Users/gumae2/Documents/Humouse/"
dfDemographics <- readRDS(str_c(pathHome, "input_data/", "gf2018noout.RDS"))
#treeVols_bilat <- readRDS(str_c(pathHome, "input_data/", "testTree.RDS"))
treeVols_LR <- readRDS(str_c(pathHome, "input_data/", "SCT-vols-no-outliers.RDS"))

source('/Users/gumae2/Documents/Humouse/input_data/tree_tools.R')
class(treeVols_LR)
```

Clone the tree so that any changes you make do not affect your original tree
```{r}
treeModel_LR <- Clone(treeVols_LR)
```

Use the pruneAnatTree() function, which takes node names and either prunes the tree at those nodes (i.e. removes them entirely), or below those nodes (i.e. removes all nodes below the given nodes). Here we  prune the ventricles and fiber tracts
```{r}
LR_tree_pruned <- Clone(treeVols_LR)
nodes_to_cut <- c("ventricular systems", "fiber tracts") #remove ventricles and cranial nerves
pruneAnatTree(LR_tree_pruned, nodes = nodes_to_cut, method = "AtNode")
```

Calculate total tissue volume
```{r}
vols_LR <- treeModel_LR$Get("volumes") %>% as_tibble
dat_LR <- vols_LR %>%  cbind(dfDemographics)

dfDemographics$shorthand <- recode_factor(dfDemographics$shorthand, XYM = "XY_M", XXYM="XXY_M", XYYM="XYY_M")
dfDemographics$ventricle_volume <- vols_LR$`ventricular systems`
dfDemographics$total_tissue_volume<- dfDemographics$brainVolume - dfDemographics$ventricle_volume
```

##Z -scoring the total tissue volume of males relative to the XY males 
```{r}
ind <- dfDemographics$genotype == "UY-Sry"
treeModel_LR$Do(function(node){
node$ctrl_mean <- mean(node$volumes[ind])
node$ctrl_sd <- sd(node$volumes[ind])
node$zscores <- (node$volumes - node$ctrl_mean)/node$ctrl_sd
})

## zscore total tissue volume
mu_ttv <- mean(dfDemographics$total_tissue_volume)
sigma_ttv <- sd(dfDemographics$total_tissue_volume)
dfDemographics$zscored_total_tissue_volume <- (dfDemographics$total_tissue_volume - mu_ttv)/sigma_ttv 
```

# Z-scored volumes

## Z-scoring the XXY and XYY males relative to the XY males
```{r}
LR_tree_pruned$Do(function(node){
#Attach metadata to the tree
    node$dfDemographics <- dfDemographics
}) 
```
### Zscore all volumes to run regular lm
```{r}
#extract volumes
#vols <- tree_pruned$Get("volumes", filterFun = isLeaf) %>% as_tibble
vols_LR <- LR_tree_pruned$Get("volumes") %>% as_tibble
#attach demographics
dfVols_LR <- cbind(dfDemographics, vols_LR)

ind_XY_M <- dfVols_LR$shorthand == 'XY_M' #First create an index getting the participants in the control group
vol_cols_all <- dfVols_LR[,16:ncol(dfVols_LR)] #Then subset the volumes for the control observations #vols from 54:461
demographics <- dfVols_LR[,1:15]
vols_XY_M <- vol_cols_all[ind_XY_M,]
df_zscores_LR <- matrix(0, nrow = nrow(vol_cols_all), ncol = ncol(vol_cols_all))
for(j in 1:ncol(vol_cols_all)){
  mu <- mean(vols_XY_M[,j]) #Then you can compute the ROI-wise averages
  sigma <- sd(vols_XY_M[,j]) #And standard deviations
  df_zscores_LR[,j] <- (vol_cols_all[,j] - mu)/sigma #Then you can use those to make the z-score volumes
}
colnames(df_zscores_LR)<-colnames(vol_cols_all)
df_zscore_LR <- demographics %>% cbind(df_zscores_LR) 
```

### Test a full model
```{r}
full_model_wTBV_LR_zscore= anatLm(~ sex+genotype + Ucount + Ycount + XXvsXY + zscored_total_tissue_volume,df_zscore_LR,df_zscore_LR[,16:ncol(df_zscore_LR)])
FDR_wTBV_LR_zscore <- anatFDR(full_model_wTBV_LR_zscore)
FDR_wTBV_LR_zscore
```

### Zscore volumes outside of the tree to run a regular linear model
```{r}
#extract volumes
#vols <- tree_pruned$Get("volumes", filterFun = isLeaf) %>% as_tibble
vols_LR <- LR_tree_pruned$Get("volumes") %>% as_tibble
#attach demographics
dfVols_LR <- cbind(dfDemographics, vols_LR)
#filter for XXY
dfVols_LR_XXY  <- dfVols_LR %>%
  filter(shorthand %in% c("XY_M", "XXY_M")) %>% 
  mutate(shorthand = factor(shorthand, levels = c("XY_M", "XXY_M")))
#filter for XYY
dfVols_LR_XYY  <- dfVols_LR %>%
  filter(shorthand %in% c("XY_M", "XYY_M")) %>% 
  mutate(shorthand = factor(shorthand, levels = c("XY_M", "XYY_M")))
```

### zscore XXY, just leaves
```{r}
ind_XY_M <- dfVols_LR_XXY$shorthand == 'XY_M' #First create an index getting the participants in the control group
vol_cols_XXY <- dfVols_LR_XXY[,16:ncol(dfVols_LR_XXY)] #Then subset the volumes for the control observations #vols from 54:461
XXY_demo <- dfVols_LR_XXY[,1:15]
vols_XY_M <- vol_cols_XXY[ind_XY_M,]
df_zscores_LR_XXY <- matrix(0, nrow = nrow(vol_cols_XXY), ncol = ncol(vol_cols_XXY))
for(j in 1:ncol(vol_cols_XXY)){
  mu <- mean(vols_XY_M[,j]) #Then you can compute the ROI-wise averages
  sigma <- sd(vols_XY_M[,j]) #And standard deviations
  df_zscores_LR_XXY[,j] <- (vol_cols_XXY[,j] - mu)/sigma #Then you can use those to make the z-score volumes
}
colnames(df_zscores_LR_XXY)<-colnames(vol_cols_XXY)
df_zscore_LR_XXY <- XXY_demo %>% cbind(df_zscores_LR_XXY) 
```

## Plot total tissue volume XXY
```{r}
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/XXY_M_TBV.pdf",   # The directory you want to save the file in
    width = 6, # The width of the plot in inches
    height = 4) # The height of the plot in inches

ggplot(dfVols_LR_XXY, aes(x = shorthand, y = zscored_total_tissue_volume, group=shorthand, colour=shorthand, fill=shorthand)) + 
  geom_flat_violin(
    position = position_nudge(x = .1, y = 0), 
    alpha =.4,adjust =0.8)+
  geom_boxplot(
    width = .1, 
    outlier.shape = NA,
     alpha = .5
  ) +
  ## add justified jitter from the {gghalves} package
  gghalves::geom_half_point(
    ## draw jitter on the left
    side = "l", 
    ## control range of jitter
    range_scale = .4, 
    ## add some transparency
    alpha = .3
  ) +
  #Adjust theme
  scale_fill_manual(values=c("#BC6E52", "#52BCA3"))+ #"#52BCA3"
  scale_color_manual(values = c("#BC6E52", "#52BCA3"))+
  theme_classic()+
  labs(
    y="Total Tissue Volume (Z-scored)",
    fill="shorthand")+  theme(text = element_text(size = 14))+ylim(-4, 4)+
  scale_y_continuous(
    sec.axis = sec_axis(name=expression(Total ~ Tissue ~ Volume ~ Volume~ (mm^3)), ~ (. * sigma_ttv) + mu_ttv), 
    name="Total Tissue Volume (Z-scored)", limits=c(-4,4)) +
  coord_cartesian(xlim = c(1.2, NA), clip = "off")
```

### zscore XYY
```{r}
ind_XY_M <- dfVols_LR_XYY$shorthand == 'XY_M' #First create an index getting the participants in the control group
vol_cols_XYY <- dfVols_LR_XYY[,16:ncol(dfVols_LR_XYY)] #Then subset the volumes for the control observations #vols from 54:461
XYY_demo <- dfVols_LR_XYY[,1:15]
vols_XY_M <- vol_cols_XYY[ind_XY_M,]
df_zscores_LR_XYY <- matrix(0, nrow = nrow(vol_cols_XYY), ncol = ncol(vol_cols_XYY))
for(j in 1:ncol(vol_cols_XYY)){
  mu <- mean(vols_XY_M[,j]) #Then you can compute the ROI-wise averages
  sigma <- sd(vols_XY_M[,j]) #And standard deviations
  df_zscores_LR_XYY[,j] <- (vol_cols_XYY[,j] - mu)/sigma #Then you can use those to make the z-score volumes
}
colnames(df_zscores_LR_XYY)<-colnames(vol_cols_XYY)
df_zscore_LR_XYY <- XYY_demo %>% cbind(df_zscores_LR_XYY) 
```

### Plot total tissue volume XYY
```{r}
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/XYY_M_TBV.pdf",   # The directory you want to save the file in
    width = 6, # The width of the plot in inches
    height = 4) # The height of the plot in inches

ggplot(dfVols_LR_XYY, aes(x = shorthand, y = zscored_total_tissue_volume, group=shorthand, colour=shorthand, fill=shorthand)) + 
geom_flat_violin(
    position = position_nudge(x = .1, y = 0), 
    alpha =.4,adjust =0.8)+
  geom_boxplot(
    width = .1, 
    outlier.shape = NA,
     alpha = .5
  ) +
  ## add justified jitter from the {gghalves} package
  gghalves::geom_half_point(
    ## draw jitter on the left
    side = "l", 
    ## control range of jitter
    range_scale = .4, 
    ## add some transparency
    alpha = .3
  ) +
  #Adjust theme
  scale_fill_manual(values=c("#BC6E52", "#6e52bc"))+
  scale_color_manual(values = c("#BC6E52", "#6e52bc"))+
 theme_classic()+
  labs(
    y="Total Tissue Volume (Z-scored)",
    fill="shorthand")+  theme(text = element_text(size = 14))+ylim(-4, 4)+
  scale_y_continuous(
    sec.axis = sec_axis(name=expression(Total ~ Tissue ~ Volume ~ Volume~ (mm^3)), ~ (. * sigma_ttv) + mu_ttv), 
    name="Total Tissue Volume (Z-scored)", limits=c(-4,4)) +
  coord_cartesian(xlim = c(1.2, NA), clip = "off")
```
## Save z-scored data as an RDS file
```{r}
saveRDS(df_zscore_LR_XXY, "/Users/gumae2/Documents/Humouse/input_data/male_XXY_zscore_LRsplit.RDS")
saveRDS(df_zscore_LR_XYY, "/Users/gumae2/Documents/Humouse/input_data/male_XYY_zscore_LRsplit.RDS")
```

## Run linear model
###With TBV covariate
XXY
```{r}
XXY_wTBV_LR_zscore= anatLm(~ shorthand + zscored_total_tissue_volume,df_zscore_LR_XXY,df_zscore_LR_XXY[,16:ncol(df_zscore_LR_XXY)])
FDR_XXY_wTBV_LR_zscore <- anatFDR(XXY_wTBV_LR_zscore)
FDR_XXY_wTBV_LR_zscore

tvals <- abs(XXY_wTBV_LR_zscore[, 'tvalue-shorthandXXY_M'])
dof <- 35
pvalsshorthandXXY_M <- 2*pt(q = tvals, df = dof, lower.tail = FALSE) %>% as_tibble()

tvals <- abs(XXY_wTBV_LR_zscore[, 'tvalue-zscored_total_tissue_volume'])
dof <- 35
pvalszscored_total_tissue_volume <- 2*pt(q = tvals, df = dof, lower.tail = FALSE) %>% as_tibble()

model_outputs_XXY_wTBV <- XXY_wTBV_LR_zscore %>% as.data.frame()
model_outputs_XXY_wTBV$label <- rownames(XXY_wTBV_LR_zscore) 
model_outputs_XXY_wTBV1 <- cbind(model_outputs_XXY_wTBV, pvalsshorthandXXY_M,pvalszscored_total_tissue_volume,FDR_XXY_wTBV_LR_zscore)
colnames(model_outputs_XXY_wTBV1) <- c("F-statistic", "R-squared", "beta-(Intercept)", "beta-shorthandXXY_M", "beta-zscored_total_tissue_volume", "tvalue-(Intercept)", "tvalue-shorthandXXY_M", "tvalue-zscored_total_tissue_volume", "logLik", "label", "pvalueshorthandXXY_M","pvaluezscored_total_tissue_volume", "qvalue-F-statistic",  "qvalue-tvalue-(Intercept)", "qvalue-tvalue-shorthandXXY_M", "qvalue-tvalue-zscored_total_tissue_volume")

write.csv(model_outputs_XXY_wTBV1, file="/Users/gumae2/Documents/Humouse_paper/Tables/XXY_M_Lm_wTBV_outputs.csv")
```

XYY
```{r}
XYY_wTBV_LR_zscore= anatLm(~ shorthand + zscored_total_tissue_volume,df_zscore_LR_XYY,df_zscore_LR_XYY[,16:ncol(df_zscore_LR_XYY)])
FDR_XYY_wTBV_LR_zscore <- anatFDR(XYY_wTBV_LR_zscore)
FDR_XYY_wTBV_LR_zscore

tvals <- abs(XYY_wTBV_LR_zscore[, 'tvalue-shorthandXYY_M'])
dof <- 38
pvalsshorthandXYY_M <- 2*pt(q = tvals, df = dof, lower.tail = FALSE) %>% as_tibble()

tvals <- abs(XYY_wTBV_LR_zscore[, 'tvalue-zscored_total_tissue_volume'])
dof <- 35
pvalszscored_total_tissue_volume <- 2*pt(q = tvals, df = dof, lower.tail = FALSE) %>% as_tibble()

model_outputs_XYY_wTBV <- XYY_wTBV_LR_zscore %>% as.data.frame()
model_outputs_XYY_wTBV$label <- rownames(XYY_wTBV_LR_zscore) 
model_outputs_XYY_wTBV1 <- cbind(model_outputs_XYY_wTBV, pvalsshorthandXYY_M,pvalszscored_total_tissue_volume,FDR_XYY_wTBV_LR_zscore)
colnames(model_outputs_XYY_wTBV1) <- c("F-statistic", "R-squared", "beta-(Intercept)", "beta-shorthandXYY_M", "beta-zscored_total_tissue_volume", "tvalue-(Intercept)", "tvalue-shorthandXYY_M", "tvalue-zscored_total_tissue_volume", "logLik", "label", "pvalueshorthandXYY_M","pvaluezscored_total_tissue_volume", "qvalue-F-statistic",  "qvalue-tvalue-(Intercept)", "qvalue-tvalue-shorthandXYY_M", "qvalue-tvalue-zscored_total_tissue_volume")

write.csv(model_outputs_XYY_wTBV1, file="/Users/gumae2/Documents/Humouse_paper/Tables/XYY_M_Lm_wTBV_outputs.csv")
```

### Without TBV covariate
XXY
```{r}
XXY_noTBV_LR_zscore= anatLm(~ shorthand, df_zscore_LR_XXY,df_zscore_LR_XXY[,16:ncol(df_zscore_LR_XXY)])
FDR_XXY_noTBV_LR_zscore <- anatFDR(XXY_noTBV_LR_zscore)
FDR_XXY_noTBV_LR_zscore

tvals <- abs(XXY_noTBV_LR_zscore[, 'tvalue-shorthandXXY_M'])
dof <- 35
pvalsshorthandXXY_M <- 2*pt(q = tvals, df = dof, lower.tail = FALSE) %>% as_tibble()

model_outputs_XXY_noTBV <- XXY_noTBV_LR_zscore %>% as.data.frame()
model_outputs_XXY_noTBV$label <- rownames(XXY_noTBV_LR_zscore) 
model_outputs_XXY_noTBV1 <- cbind(model_outputs_XXY_noTBV, pvalsshorthandXXY_M,FDR_XXY_noTBV_LR_zscore)
colnames(model_outputs_XXY_noTBV1) <- c("F-statistic","R-squared","beta-(Intercept)","beta-shorthandXXY_M","tvalue-(Intercept)", "tvalue-shorthandXXY_M","logLik","label","pvalueshorthandXXY_M","qvalue-F-statistic", "qvalue-tvalue-(Intercept)","qvalue-tvalue-shorthandXXY_M")

write.csv(model_outputs_XXY_noTBV1, file="/Users/gumae2/Documents/Humouse_paper/Tables/XXY_M_Lm_noTBV_outputs.csv")
```
XYY
```{r}
XYY_noTBV_LR_zscore= anatLm(~ shorthand,df_zscore_LR_XYY,df_zscore_LR_XYY[,16:ncol(df_zscore_LR_XYY)])
FDR_XYY_noTBV_LR_zscore <- anatFDR(XYY_noTBV_LR_zscore)
#summary_XYY_noTBV_zscore <- summary(XYY_noTBV_zscore)
FDR_XYY_noTBV_LR_zscore

tvalsXYY <- abs(XYY_noTBV_LR_zscore[, 'tvalue-shorthandXYY_M'])
dof <- 38
pvalsshorthandXYY_M <- 2*pt(q = tvalsXYY, df = dof, lower.tail = FALSE) %>% as_tibble()

model_outputs_XYY_noTBV <- XYY_noTBV_LR_zscore %>% as.data.frame()
model_outputs_XYY_noTBV$label <- rownames(XYY_noTBV_LR_zscore) 
model_outputs_XYY_noTBV1 <- cbind(model_outputs_XYY_noTBV, pvalsshorthandXYY_M,FDR_XYY_noTBV_LR_zscore)
colnames(model_outputs_XYY_noTBV1) <- c("F-statistic","R-squared","beta-(Intercept)","beta-shorthandXYY_M","tvalue-(Intercept)", "tvalue-shorthandXYY_M","logLik","label","pvalueshorthandXYY_M", "qvalue-F-statistic", "qvalue-tvalue-(Intercept)","qvalue-tvalue-shorthandXYY_M")
write.csv(model_outputs_XYY_noTBV1, file="/Users/gumae2/Documents/Humouse_paper/Tables/XYY_M_Lm_noTBV_outputs.csv")

model_outputs_both_groups <- merge(model_outputs_XXY_wTBV1, model_outputs_XYY_wTBV1, by="label")
write.csv(model_outputs_both_groups, file="/Users/gumae2/Documents/Humouse_paper/Tables/M_Lm_wTBV_outputs.csv")

model_outputs_both_groups <- merge(model_outputs_XXY_noTBV1, model_outputs_XYY_noTBV1, by="label")
write.csv(model_outputs_both_groups, file="/Users/gumae2/Documents/Humouse_paper/Tables/M_Lm_noTBV_outputs.csv")
```


## Calculate zscores across all nodes in the tree, run the model, and extract the beta coefficients
```{r}
#Run our anonymous function at every node
LR_tree_pruned$Do(function(node){
#Run our anonymous function at every node
#tree_pruned$Do(function(node){
  #Assign 
  node$dfModel <- dfDemographics %>%
    dplyr::select(sex, shorthand, brainVolume, total_tissue_volume)

  #Create a data frame that contains sex, shorthand, brainVolume, and volumes
  node$dfModel <- node$dfModel %>%
    mutate(volumes = node$volumes)
  
  #Filter for males and not XXM
  node$dfModel <- node$dfModel %>%
    filter(sex == "M",
           shorthand != "XXM")

  #Create a separate data frame for XXY_M
  node$dfModel_XXY_M  <- node$dfModel %>%
    filter(shorthand %in% c("XY_M", "XXY_M"))
  
  #Create a separate data frame for XYY_M
  node$dfModel_XYY_M  <- node$dfModel %>%
    filter(shorthand %in% c("XY_M", "XYY_M"))

  #Level the shorthand variables as desired
  node$dfModel_XXY_M <- node$dfModel_XXY_M %>% 
    mutate(shorthand = factor(shorthand, levels = c("XY_M", "XXY_M")))
  node$dfModel_XYY_M <- node$dfModel_XYY_M %>% 
    mutate(shorthand = factor(shorthand, levels = c("XY_M", "XYY_M")))

  #Compute the volume mean for XXY_M controls
  node$meanVolume_XXY_M <- node$dfModel_XXY_M %>% 
    filter(shorthand == "XY_M") %>%  #Filter for controls
    pull(volumes) %>%               #Extract the column volumes as a vector
    mean()                          #Calculate the mean on the volumes vector
  
  #Compute the volume sd for XXY_M controls
  node$sdVolume_XXY_M <- node$dfModel_XXY_M %>% 
    filter(shorthand == "XY_M") %>% 
    pull(volumes) %>% 
    sd()
 
  #Compute the total volume mean for XXY_M controls
  node$meanTotalVolume_XXY_M <- node$dfModel_XXY_M %>% 
    filter(shorthand == "XY_M") %>% 
    pull(brainVolume) %>% 
    mean()
 
  #Compute the total volume sd for XXY_M controls
  node$sdTotalVolume_XXY_M <- node$dfModel_XXY_M %>% 
    filter(shorthand == "XY_M") %>% 
    pull(brainVolume) %>% 
    sd()
  
   #Compute the total tissue volume mean for XXY_M controls
  node$meanTotalTissueVolume_XXY_M <- node$dfModel_XXY_M %>% 
    filter(shorthand == "XY_M") %>% 
    pull(total_tissue_volume) %>% 
    mean()
 
  #Compute the total tissue volume sd for XXY_M controls
  node$sdTotalTissueVolume_XXY_M <- node$dfModel_XXY_M %>% 
    filter(shorthand == "XY_M") %>% 
    pull(total_tissue_volume) %>% 
    sd()
  
  #Compute the volume mean for XYY_M controls
  node$meanVolume_XYY_M <- node$dfModel_XYY_M %>% 
    filter(shorthand == "XY_M") %>%  #Filter for controls
    pull(volumes) %>%               #Extract the column volumes as a vector
    mean()                          #Calculate the mean on the volumes vector
  
  #Compute the volume sd for XYY_M controls
  node$sdVolume_XYY_M <- node$dfModel_XYY_M %>% 
    filter(shorthand == "XY_M") %>% 
    pull(volumes) %>% 
    sd()
  
  #Compute the total volume mean for XYY_M controls
  node$meanTotalVolume_XYY_M <- node$dfModel_XYY_M %>% 
    filter(shorthand == "XY_M") %>% 
    pull(brainVolume) %>% 
    mean()
  
  #Compute the total volume sd for XYY_M controls
  node$sdTotalVolume_XYY_M <- node$dfModel_XYY_M %>% 
    filter(shorthand == "XY_M") %>% 
    pull(brainVolume) %>% 
    sd()

    #Compute the total volume mean for XYY_M controls
  node$meanTotalTissueVolume_XYY_M <- node$dfModel_XYY_M %>% 
    filter(shorthand == "XY_M") %>% 
    pull(total_tissue_volume) %>% 
    mean()
  
  #Compute the total volume sd for XYY_M controls
  node$sdTotalTissueVolume_XYY_M <- node$dfModel_XYY_M %>% 
    filter(shorthand == "XY_M") %>% 
    pull(total_tissue_volume) %>% 
    sd()
  
  #Compute z-scores for XXY_M
  node$dfModel_XXY_M <- node$dfModel_XXY_M %>% 
    mutate(volumes_zscore = (volumes - node$meanVolume_XXY_M)/node$sdVolume_XXY_M,
           brainVolume_zscore = (brainVolume - node$meanTotalVolume_XXY_M)/node$sdTotalVolume_XXY_M,
           totalTissueVol_zscore= (total_tissue_volume - node$meanTotalTissueVolume_XXY_M)/node$sdTotalTissueVolume_XXY_M)
  
  #Compute z-scores for XYY_M
  node$dfModel_XYY_M <- node$dfModel_XYY_M %>% 
    mutate(volumes_zscore = (volumes - node$meanVolume_XYY_M)/node$sdVolume_XYY_M,
           brainVolume_zscore = (brainVolume - node$meanTotalVolume_XYY_M)/node$sdTotalVolume_XYY_M,
           totalTissueVol_zscore= (total_tissue_volume - node$meanTotalTissueVolume_XYY_M)/node$sdTotalTissueVolume_XYY_M)

  #Compute linear models with TBV correction
  node$model_XXY_M_wTBV <- lm(volumes_zscore ~ shorthand + totalTissueVol_zscore, data = node$dfModel_XXY_M)
  node$model_XYY_M_wTBV <- lm(volumes_zscore ~ shorthand + totalTissueVol_zscore, data = node$dfModel_XYY_M)

  #Compute linear models without TBV correction
  node$model_XXY_M_noTBV <- lm(volumes_zscore ~ shorthand, data = node$dfModel_XXY_M)
  node$model_XYY_M_noTBV <- lm(volumes_zscore ~ shorthand, data = node$dfModel_XYY_M)
 
  #Compute linear model summaries
  #with TBV
  node$model_summary_XXY_M_wTBV  <- summary(node$model_XXY_M_wTBV )
  node$model_summary_XYY_M_wTBV  <- summary(node$model_XYY_M_wTBV )
  #without TBV
  node$model_summary_XXY_M_noTBV  <- summary(node$model_XXY_M_noTBV )
  node$model_summary_XYY_M_noTBV  <- summary(node$model_XYY_M_noTBV )

  #Extract shorthand beta parameter estimates
  #with TBV
  node$beta_shorthand_XXY_M_wTBV  <- node$model_summary_XXY_M_wTBV $coefficients["shorthandXXY_M", "Estimate"]
  node$beta_shorthand_XYY_M_wTBV  <- node$model_summary_XYY_M_wTBV $coefficients["shorthandXYY_M", "Estimate"]
  node$tvalue_shorthand_XXY_M_wTBV  <- node$model_summary_XXY_M_wTBV $coefficients["shorthandXXY_M", "t value"]
  node$tvalue_shorthand_XYY_M_wTBV  <- node$model_summary_XYY_M_wTBV $coefficients["shorthandXYY_M", "t value"]
  node$pvalue_shorthand_XXY_M_wTBV  <- node$model_summary_XXY_M_wTBV $coefficients["shorthandXXY_M", "Pr(>|t|)"]
  node$pvalue_shorthand_XYY_M_wTBV  <- node$model_summary_XYY_M_wTBV $coefficients["shorthandXYY_M", "Pr(>|t|)"]
 
  #no TBV
  node$beta_shorthand_XXY_M_noTBV  <- node$model_summary_XXY_M_noTBV $coefficients["shorthandXXY_M", "Estimate"]
  node$beta_shorthand_XYY_M_noTBV  <- node$model_summary_XYY_M_noTBV $coefficients["shorthandXYY_M", "Estimate"]
  node$tvalue_shorthand_XXY_M_noTBV  <- node$model_summary_XXY_M_noTBV $coefficients["shorthandXXY_M", "t value"]
  node$tvalue_shorthand_XYY_M_noTBV  <- node$model_summary_XYY_M_noTBV $coefficients["shorthandXYY_M", "t value"]
  node$pvalue_shorthand_XXY_M_noTBV  <- node$model_summary_XXY_M_noTBV $coefficients["shorthandXXY_M", "Pr(>|t|)"]
  node$pvalue_shorthand_XYY_M_noTBV  <- node$model_summary_XYY_M_noTBV $coefficients["shorthandXYY_M", "Pr(>|t|)"]
 })
```

If we want to extract those values from the tree, we can use the $Get() method. This “gets” the field specified for every node:
```{r}
#With TBV correction
totalTissueVolume <- LR_tree_pruned$Get("totalTissueVol_zscore")
beta_shorthand_XXY_M_wTBV <- LR_tree_pruned$Get("beta_shorthand_XXY_M_wTBV") 
beta_shorthand_XYY_M_wTBV <- LR_tree_pruned$Get("beta_shorthand_XYY_M_wTBV")  
# beta_shorthand_XXY_M_wTBV_leaves <- LR_tree_pruned$Get("beta_shorthand_XXY_M_wTBV", filterFun = isLeaf)  
# beta_shorthand_XYY_M_wTBV_leaves <- LR_tree_pruned$Get("beta_shorthand_XYY_M_wTBV", filterFun = isLeaf)  
tvalue_shorthand_XXY_M_wTBV <- LR_tree_pruned$Get("tvalue_shorthand_XXY_M_wTBV") 
tvalue_shorthand_XYY_M_wTBV <- LR_tree_pruned$Get("tvalue_shorthand_XYY_M_wTBV")
pvalue_shorthand_XXY_M_wTBV <- LR_tree_pruned$Get("pvalue_shorthand_XXY_M_wTBV") 
pvalue_shorthand_XYY_M_wTBV <- LR_tree_pruned$Get("pvalue_shorthand_XYY_M_wTBV") 
#Without TBV correction
beta_shorthand_XXY_M_noTBV <- LR_tree_pruned$Get("beta_shorthand_XXY_M_noTBV")
beta_shorthand_XYY_M_noTBV <- LR_tree_pruned$Get("beta_shorthand_XYY_M_noTBV")
# beta_shorthand_XXY_M_noTBV_leaves <- LR_tree_pruned$Get("beta_shorthand_XXY_M_noTBV", filterFun = isLeaf)
# beta_shorthand_XYY_M_noTBV_leaves <- LR_tree_pruned$Get("beta_shorthand_XYY_M_noTBV", filterFun = isLeaf) 
tvalue_shorthand_XXY_M_noTBV <- LR_tree_pruned$Get("tvalue_shorthand_XXY_M_noTBV") 
tvalue_shorthand_XYY_M_noTBV <- LR_tree_pruned$Get("tvalue_shorthand_XYY_M_noTBV") 
pvalue_shorthand_XXY_M_noTBV <- LR_tree_pruned$Get("pvalue_shorthand_XXY_M_noTBV") 
pvalue_shorthand_XYY_M_noTBV <- LR_tree_pruned$Get("pvalue_shorthand_XYY_M_noTBV") 
```

```{r}
## Save z-scored data as an RDS file
saveRDS(beta_shorthand_XXY_M_wTBV, "/Users/gumae2/Documents/Humouse/input_data/male_XXY_beta_values_LRsplit.RDS")
saveRDS(beta_shorthand_XYY_M_wTBV, "/Users/gumae2/Documents/Humouse/input_data/male_XYY_beta_values_LRsplit.RDS")
```


## Plot results
Threshold regions that are significant at an uncorrected p<0.05 threshold.
XXY with TBV correction
```{r}
## Threshold at p=0.05
df_pvalue_shorthand_XXY_M_wTBV <- pvalue_shorthand_XXY_M_wTBV %>% enframe(name = "Region", value = "pvalue_shorthand_XXY_M_wTBV") %>% as_tibble()
df_beta_shorthand_XXY_M_wTBV <- beta_shorthand_XXY_M_wTBV %>% enframe(name = "Region", value = "beta_shorthand_XXY_M_wTBV") %>% as_tibble()

sig_pvalues_pos_XXY_wTBV <- df_pvalue_shorthand_XXY_M_wTBV$pvalue_shorthand_XXY_M_wTBV < 0.048
sig_pvalues_neg_XXY_wTBV <- df_pvalue_shorthand_XXY_M_wTBV$pvalue_shorthand_XXY_M_wTBV< -0.048
sig_beta_XXY_wTBV <- df_beta_shorthand_XXY_M_wTBV[sig_pvalues_pos_XXY_wTBV | sig_pvalues_neg_XXY_wTBV, ]

sig_beta_XXY_tree<-left_join(df_beta_shorthand_XXY_M_wTBV, sig_beta_XXY_wTBV, by = "Region")
filtered_sig_beta_XXY_tree <- subset(sig_beta_XXY_tree, select = c("Region","beta_shorthand_XXY_M_wTBV.y"))
sig_beta_XXY_wTBV$Region

LR_tree_pruned$Do(function(node){
  ind <- which(filtered_sig_beta_XXY_tree$Region == node$name)
  node$XXY_beta_p05_wTBV <- filtered_sig_beta_XXY_tree$beta_shorthand_XXY_M_wTBV.y[ind]
})
```

XYY with TBV correction
```{r}
## Threshold at p=0.05
df_pvalue_shorthand_XYY_M_wTBV <- pvalue_shorthand_XYY_M_wTBV %>% enframe(name = "Region", value = "pvalue_shorthand_XYY_M_wTBV") %>% as_tibble()
df_beta_shorthand_XYY_M_wTBV <- beta_shorthand_XYY_M_wTBV %>% enframe(name = "Region", value = "beta_shorthand_XYY_M_wTBV") %>% as_tibble()

sig_pvalues_pos_XYY_wTBV <- df_pvalue_shorthand_XYY_M_wTBV$pvalue_shorthand_XYY_M_wTBV < 0.049
sig_pvalues_neg_XYY_wTBV <- df_pvalue_shorthand_XYY_M_wTBV$pvalue_shorthand_XYY_M_wTBV< -0.049
sig_beta_XYY_wTBV <- df_beta_shorthand_XYY_M_wTBV[sig_pvalues_pos_XYY_wTBV | sig_pvalues_neg_XYY_wTBV, ]

sig_beta_XYY_wTBV_tree<-left_join(df_beta_shorthand_XYY_M_wTBV, sig_beta_XYY_wTBV, by = "Region")
filtered_sig_beta_XYY_wTBV_tree <- subset(sig_beta_XYY_wTBV_tree, select = c("Region","beta_shorthand_XYY_M_wTBV.y"))
sig_beta_XYY_wTBV$Region

LR_tree_pruned$Do(function(node){
  ind <- which(filtered_sig_beta_XYY_wTBV_tree$Region == node$name)
  node$XYY_beta_p05_wTBV <- filtered_sig_beta_XYY_wTBV_tree$beta_shorthand_XYY_M_wTBV.y[ind]
})
```


## Read in the label and anatomical volumes
```{r} 
labelVol <- mincArray(mincGetVolume("/Users/gumae2/Documents/Humouse/input_data/DSURQE_40micron_labels.mnc"))
anatVol <- mincArray(mincGetVolume("/Users/gumae2/Documents/Humouse/input_data/DSURQE_40micron_average.mnc"))
labelCols <- hanatToVolume(treeModel_LR, labelVol, "color_hex_triplet") #load in the Allen atlas colours to display next to the results
```


Assign colour palette for positive and negative beta values 
```{r}
positive_cols <- function() {
  getOption("MRIcrotomeCol", colorRampPalette(c("yellow","red","firebrick"))(255))
}

negative_cols <- function() {
  getOption("MRIcrotomeRcol", colorRampPalette(c("turquoise3","royalblue","navyblue"))(255))
}
```

## Results without TBV correction
### Thresholded maps at p=0.05 without TBV correction
Beta-value plots for XXY and XYY with TBV correction
```{r}
## load in beta values from the tree
XXY_M_beta_wTBV_unthresholded <- hanatToVolume(LR_tree_pruned, labelVol, "beta_shorthand_XXY_M_wTBV")
XXY_M_beta_wTBV_p05 <- hanatToVolume(LR_tree_pruned, labelVol, "XXY_beta_p05_wTBV") #turn the t-value back into a volume file

XYY_M_beta_wTBV_unthresholded <- hanatToVolume(LR_tree_pruned, labelVol, "beta_shorthand_XYY_M_wTBV") #turn the t-value back into a volume file
XYY_M_beta_wTBV_p05 <- hanatToVolume(LR_tree_pruned, labelVol, "XYY_beta_p05_wTBV") #turn the t-value back into a volume file

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/XXY_XYY_unthresh_thres_wTBV_nowm_LR_split_8.pdf",   # The directory you want to save the file in
    width = 7.5, # The width of the plot in inches
    height = 6.5) # The height of the plot in inches
sliceSeries(nrow=8, ncol=1, begin=70, end=350) %>%
  anatomy(anatVol, low=700, high=1400) %>% overlay(labelCols, low=0, high=1) %>% addtitle("Atlas") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(XXY_M_beta_wTBV_unthresholded, low=0, high=1.5, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>% addtitle("XXY_M") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(XXY_M_beta_wTBV_p05, low=0, high=1.5, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>%
  addtitle("p<0.05") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(XYY_M_beta_wTBV_unthresholded, low=0, high=1.5, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>% addtitle("XYY_M ") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(XYY_M_beta_wTBV_p05, low=0, high=1.5, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>%
  legend("Beta-value (with TTV correction") %>% addtitle("p<0.05") %>% draw()
```

## Results without TBV correction
Thresholded maps at p=0.05 without TBV correction
XYY with TBV
```{r}
## Threshold at p=0.05
df_pvalue_shorthand_XXY_M_noTBV <- pvalue_shorthand_XXY_M_noTBV %>% enframe(name = "Region", value = "pvalue_shorthand_XXY_M_noTBV") %>% as_tibble()
df_beta_shorthand_XXY_M_noTBV <- beta_shorthand_XXY_M_noTBV %>% enframe(name = "Region", value = "beta_shorthand_XXY_M_noTBV") %>% as_tibble()

sig_pvalues_pos_XXY_noTBV <- df_pvalue_shorthand_XXY_M_noTBV$pvalue_shorthand_XXY_M_noTBV < 0.049
sig_pvalues_neg_XXY_noTBV <- df_pvalue_shorthand_XXY_M_noTBV$pvalue_shorthand_XXY_M_noTBV< -0.049
sig_beta_XXY_noTBV <- df_beta_shorthand_XXY_M_noTBV[sig_pvalues_pos_XXY_noTBV | sig_pvalues_neg_XXY_noTBV, ]

sig_beta_XXY_treenoTBV<-left_join(df_beta_shorthand_XXY_M_noTBV, sig_beta_XXY_noTBV, by = "Region")
filtered_sig_beta_XXY_treenoTBV <- subset(sig_beta_XXY_treenoTBV, select = c("Region","beta_shorthand_XXY_M_noTBV.y"))
sig_beta_XXY_noTBV$Region

LR_tree_pruned$Do(function(node){
  ind <- which(filtered_sig_beta_XXY_treenoTBV$Region == node$name)
  node$XXY_beta_p05_noTBV <- filtered_sig_beta_XXY_treenoTBV$beta_shorthand_XXY_M_noTBV.y[ind]
})
```

XYY without TBV
```{r}
## Threshold at p=0.05
df_pvalue_shorthand_XYY_M_noTBV <- pvalue_shorthand_XYY_M_noTBV %>% enframe(name = "Region", value = "pvalue_shorthand_XYY_M_noTBV") %>% as_tibble()
df_beta_shorthand_XYY_M_noTBV <- beta_shorthand_XYY_M_noTBV %>% enframe(name = "Region", value = "beta_shorthand_XYY_M_noTBV") %>% as_tibble()

sig_pvalues_pos_XYY_noTBV <- df_pvalue_shorthand_XYY_M_noTBV$pvalue_shorthand_XYY_M_noTBV < 0.049
sig_pvalues_neg_XYY_noTBV <- df_pvalue_shorthand_XYY_M_noTBV$pvalue_shorthand_XYY_M_noTBV< -0.049
sig_beta_XYY_noTBV <- df_beta_shorthand_XYY_M_noTBV[sig_pvalues_pos_XYY_noTBV | sig_pvalues_neg_XYY_noTBV, ]

sig_beta_XYY_noTBV_tree<-left_join(df_beta_shorthand_XYY_M_noTBV, sig_beta_XYY_noTBV, by = "Region")
filtered_sig_beta_XYY_noTBV_tree <- subset(sig_beta_XYY_noTBV_tree, select = c("Region","beta_shorthand_XYY_M_noTBV.y"))
sig_beta_XYY_noTBV$Region

LR_tree_pruned$Do(function(node){
  ind <- which(filtered_sig_beta_XYY_noTBV_tree$Region == node$name)
  node$XYY_beta_p05_noTBV <- filtered_sig_beta_XYY_noTBV_tree$beta_shorthand_XYY_M_noTBV.y[ind]
})
```

Beta-value plots for XXY and XYY with TBV correction
```{r}
## load in beta values from the tree
XXY_M_beta_noTBV_unthresholded <- hanatToVolume(LR_tree_pruned, labelVol, "beta_shorthand_XXY_M_noTBV") #turn the b-value back into a volume file
XXY_M_beta_noTBV_p05 <- hanatToVolume(LR_tree_pruned, labelVol, "XXY_beta_p05_noTBV") #turn the t-value back into a volume file

XYY_M_beta_noTBV_unthresholded <- hanatToVolume(LR_tree_pruned, labelVol, "beta_shorthand_XYY_M_noTBV") #turn the t-value back into a volume file
XYY_M_beta_noTBV_p05 <- hanatToVolume(LR_tree_pruned, labelVol, "XYY_beta_p05_noTBV") #turn the t-value back into a volume file

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/XXY_XYY_unthresh_thres_noTBV_nowm_LRsplit_8.pdf",   # The directory you want to save the file in
   width = 7.5, # The width of the plot in inches
    height = 6.5) # The height of the plot in inches
sliceSeries(nrow=8, ncol=1, begin=70, end=350) %>%
  anatomy(anatVol, low=700, high=1400) %>% overlay(labelCols, low=0, high=1) %>% addtitle("Atlas") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(XXY_M_beta_noTBV_unthresholded, low=0, high=1.5, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>% addtitle("XXY_M") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(XXY_M_beta_noTBV_p05, low=0, high=1.5, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>%
  addtitle("p<0.05") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(XYY_M_beta_noTBV_unthresholded, low=0, high=1.5, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>% addtitle("XYY_M ") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(XYY_M_beta_noTBV_p05, low=0, high=1.5, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>%
  legend("Beta-value (with TTV correction") %>% addtitle("p<0.05") %>% draw()
```


## Density plot of beta values with TBV
```{r}
library(reshape2)
# plot
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/XXY_XYY_mean_beta_density_wTBV_nowm.pdf",
     width = 5,
     height = 4)

##With TBV
## merge the dataframes with beta values for the leaves (with TBV correction)
betas <- cbind(beta_shorthand_XXY_M_wTBV, beta_shorthand_XYY_M_wTBV)
label <- LR_tree_pruned$Get("name") %>% as_tibble()
df_betas <-cbind(label, betas) 
colnames(df_betas) <- c("label", "XXY_M", "XYY_M")
## stack the columns containing the beta values for plotting
df_betas_long <- melt(df_betas, id.var = c('label'), variable.name = 'beta_value')
write.csv(df_betas_long, file="/Users/gumae2/Documents/Humouse_paper/Tables/mouse_betas_wTBV.csv")
## calculate the mean per group to plot the vertical line
df_beta_long_1 <-df_betas_long %>% group_by(beta_value) %>% summarize(mean=mean(value))
## plot
ggplot(df_betas_long, aes(x=value, fill=beta_value, color=beta_value)) +
    geom_density(alpha=.3) +
    scale_fill_manual(labels = c("XXY_M", "XYY_M"), name="Beta", values=c('#52BCA3', '#6e52bc'))+
    scale_color_manual(label=NULL,name=NULL,guide=NULL, values = c('#52BCA3', '#6e52bc'))+
    theme_classic()+ xlab("Beta-value (with TTV correction)")+ylab("Density")+
    theme(text = element_text(size = 14))+xlim(-1.5,1.5)+ylim(0,2)+
    geom_vline(data=df_beta_long_1, aes(xintercept=mean, color=beta_value),
             linetype="dashed") +
    geom_vline(xintercept=c(0))

```
## Without TBV correction
```{r}
##NO TBV
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/XXY_XYY_mean_beta_density_noTBV_nowm.pdf",
     width = 5,
     height = 4)

betas_noTBV <- cbind(beta_shorthand_XXY_M_noTBV, beta_shorthand_XYY_M_noTBV)
df_betas_noTBV <-cbind(label, betas_noTBV) 
colnames(df_betas_noTBV) <- c("label", "XXY_M", "XYY_M")
## stack the columns containing the beta values for plotting
df_betas_long_noTBV <- melt(df_betas_noTBV, id.var = c('label'), variable.name = 'beta_value')
write.csv(df_betas_long_noTBV, file="/Users/gumae2/Documents/Humouse_paper/Tables/mouse_betas_noTBV.csv")
## calculate the mean per group to plot the vertical line
df_beta_noTBV_long_1 <-df_betas_long_noTBV %>% group_by(beta_value) %>% summarize(mean=mean(value))
## plot
ggplot(df_betas_long_noTBV, aes(x=value, fill=beta_value, color=beta_value)) +
    geom_density(alpha=.3) +
    geom_vline(data=df_beta_noTBV_long_1, aes(xintercept=mean, color=beta_value),
             linetype="dashed")+
 scale_fill_manual(labels = c("XXY_M", "XYY_M"), name="Beta",values=c('#52BCA3', '#6e52bc'))+
  scale_color_manual(label=NULL,name=NULL,guide=NULL,values = c('#52BCA3', '#6e52bc'))+
   theme_classic()+ xlab("Beta-value (no TTV correction)")+ylab("Density")+
   theme(text = element_text(size = 14))+xlim(-1.5,1.5)+ylim(0,2)+
    geom_vline(xintercept=c(0))
```
