---
title: "Female-split-half-LR"
author: "Elisa Guma"
date: "4/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## R Markdown
```{r }
library(tidyverse)
library(data.tree)
library(RMINC)
library(magrittr)
library(ggplot2)
library(MRIcrotome)
```


```{r}
pathHome <- "/Users/gumae2/Documents/Humouse/"
demographics <- readRDS(str_c(pathHome, "input_data/", "gf2018noout.RDS"))
treeVols_bilat <- readRDS(str_c(pathHome, "input_data/", "testTree.RDS"))
treeVols_LR <- readRDS(str_c(pathHome, "input_data/", "SCT-vols-no-outliers.RDS"))

source('/Users/gumae2/Documents/Humouse/input_data/tree_tools.R')
```

# Gonadal Females
Calculate total tissue volume
```{r}
vols <- treeVols_LR$Get("volumes") %>% as_tibble
dat <- vols %>%  cbind(demographics)

demographics$shorthand <- recode_factor(demographics$shorthand, XYF = "XY_MF", XXYF="XXY_MF", XYYF="XYY_MF")
demographics$ventricle_volume <- vols$`ventricular systems`
demographics$total_tissue_volume<- demographics$brainVolume - demographics$ventricle_volume
```

```{r}
LR_tree_pruned <- Clone(treeVols_LR)
nodes_to_cut <- c("ventricular systems", "fiber tracts") #remove ventricles and cranial nerves
pruneAnatTree(LR_tree_pruned, nodes = nodes_to_cut, method = "AtNode")
treeTest <- FindNode(treeVols_LR, "Thalamus")
```

## Select the rows from the demographics dataset that correspond to the groups of interest
```{r}
rows_just_xy <- which(demographics$shorthand == "XY_MF")
rows_XXYF <- which(demographics$shorthand == "XXY_MF")
rows_XYYF <- which(demographics$shorthand == "XYY_MF")
```
## Assign the number of samples
```{r}
nsamples <-1000
```

### Sample indices for half of the rows corresponding to UY-Sry
```{r}
#set.seed(42)
listSampleIndices <- vector(mode = "list", length = nsamples)
for(i in 1:nsamples){
  listSampleIndices[[i]] = sample(x = 1:length(rows_just_xy), size = 0.5*length(rows_just_xy), replace = FALSE)
}
```

#### Next we compute the split-half zscores in the tree
```{r}
#This is done at each node
LR_tree_pruned$Do(function(node){
    #For the given node, iterate over our permutations
   #Attach metadata to the tree
    node$demographics <- demographics
    node$genotype <- demographics$genotype
    node$brainVolume <- demographics$brainVolume
    node$tissueVolume <- demographics$total_tissue_volume
    node$shorthand <- demographics$shorthand
    node$sex <- demographics$sex

   #initialize vectors in which to store the betas from linear model
    node$beta_A_f <- numeric(nsamples)
    node$beta_B_f <- numeric(nsamples)
    node$beta_A_f_noTBV <- numeric(nsamples)
    node$beta_B_f_noTBV <- numeric(nsamples)
    
   #initialize vectors in which to store the sigma-betas from linear model
    node$sigma_beta_A_m <- numeric(nsamples)
    node$sigma_beta_B_m <- numeric(nsamples)
    node$sigma_beta_A_m_noTBV <- numeric(nsamples)
    node$sigma_beta_B_m_noTBV <- numeric(nsamples)
  
  for(i in 1:nsamples){
    #Using the sampled indices, extract the sets of rows corresponding to XY entries    
    rows_xy_sampleA <- rows_just_xy[listSampleIndices[[i]]] #sample A are the rows that are selected in the listSampleIndices above
    rows_xy_sampleB <- rows_just_xy[-listSampleIndices[[i]]] #sample B are the remaining rows 

    rows_XXYF <- which(demographics$shorthand == "XXY_MF") #select the XXY row (redundant from above)
    rows_XYYF <- which(demographics$shorthand == "XYY_MF") #select the XYY rows 
    
    rows_sampleA<-c(rows_XXYF, rows_xy_sampleA)
    rows_sampleB<-c(rows_XYYF, rows_xy_sampleB)
 
    #Compute the zscores for all volumes and store them in the correct position in the node
    #calculate the mean for XY sample A for each volume in the node
    node$ctrl_mean_sampleA <- mean(node$volumes[rows_xy_sampleA]) 
    node$ctrl_sd_sampleA <- sd(node$volumes[rows_xy_sampleA]) #same for the sd
    node$zscores_sampleA <- (node$volumes - node$ctrl_mean_sampleA)/node$ctrl_sd_sampleA #zscore relative to XY sample A
   #repeat for sample B
    node$ctrl_mean_sampleB <- mean(node$volumes[rows_xy_sampleB])
    node$ctrl_sd_sampleB <- sd(node$volumes[rows_xy_sampleB])
    node$zscores_sampleB  <- (node$volumes - node$ctrl_mean_sampleB)/node$ctrl_sd_sampleB #zscore relative to XY sample B
   
   #calculate TBV
   #calculate the z-scored brain volume with the newly split controls
   node$mean_tissueVolume_sampleA <- mean(node$tissueVolume[rows_xy_sampleA])
   node$sd_tissueVolume_sampleA <- sd(node$tissueVolume[rows_xy_sampleA])
   node$zscored_tissueVolume_sampleA <- (node$tissueVolume - node$mean_tissueVolume_sampleA)/node$sd_tissueVolume_sampleA
   node$mean_tissueVolume_sampleB <- mean(node$tissueVolume[rows_xy_sampleB])
   node$sd_tissueVolume_sampleB <- sd(node$tissueVolume[rows_xy_sampleB])
   node$zscored_tissueVolume_sampleB <- (node$tissueVolume - node$mean_tissueVolume_sampleB)/node$sd_tissueVolume_sampleB

    #load in the computed z-scores
   node$model_df_A <- node$demographics %>% mutate(zscores_A = node$zscores_sampleA) %>% mutate(zscored_tissueVolume_A = node$zscored_tissueVolume_sampleA) %>% mutate(shorthand = factor(shorthand, levels = c("XY_MF", "XXY_MF")))
   node$model_df_B <- node$demographics %>% mutate(zscores_B = node$zscores_sampleB) %>% mutate(zscored_tissueVolume_B = node$zscored_tissueVolume_sampleB) %>% mutate(shorthand = factor(shorthand, levels = c("XY_MF", "XYY_MF")))

  #load in the computed z-scores
   node$model_df_A_noTBV <- node$model_df_A
   node$model_df_B_noTBV <- node$model_df_B

#subset the correct rows
  node$model_df_A <- node$model_df_A[rows_sampleA, ]
  node$model_df_B <- node$model_df_B[rows_sampleB, ]
  node$model_df_A_noTBV <- node$model_df_A_noTBV[rows_sampleA, ]
  node$model_df_B_noTBV <- node$model_df_B_noTBV[rows_sampleB, ]

#run the linear model
  node$model_A <- summary(lm(zscores_A ~ shorthand + zscored_tissueVolume_A, data = node$model_df_A))
  node$model_B <- summary(lm(zscores_B ~ shorthand + zscored_tissueVolume_B, data = node$model_df_B))
  node$model_A_noTBV <- summary(lm(zscores_A ~ shorthand , data = node$model_df_A_noTBV))
  node$model_B_noTBV <- summary(lm(zscores_B ~ shorthand , data = node$model_df_B_noTBV))

#store the beta coefficients
  node$beta_A_f[i] <- node$model_A$coefficients["shorthandXXY_MF", "Estimate"]
  node$beta_B_f[i] <- node$model_B$coefficients["shorthandXYY_MF", "Estimate"]
  node$beta_A_f_noTBV[i] <- node$model_A_noTBV$coefficients["shorthandXXY_MF", "Estimate"]
  node$beta_B_f_noTBV[i] <- node$model_B_noTBV$coefficients["shorthandXYY_MF", "Estimate"]
  }
})
```



## Extract 

## Beta values for each linear model at the leaves for models with and without TBV correction
```{r}
Beta_sampleA_Females_withTVB <- LR_tree_pruned$Get("beta_A_f", filterFun = isLeaf) %>% as_tibble()
Beta_sampleB_Females_withTVB <- LR_tree_pruned$Get("beta_B_f", filterFun = isLeaf) %>% as_tibble()
Beta_sampleA_Females_noTBV <- LR_tree_pruned$Get("beta_A_f_noTBV", filterFun = isLeaf) %>% as_tibble()
Beta_sampleB_Females_noTBV <- LR_tree_pruned$Get("beta_B_f_noTBV", filterFun = isLeaf) %>% as_tibble()
```

### Beta values for each linear model across the whole tree with and without TBV correction
```{r}
Beta_sampleA_Females_tree_withTVB <- LR_tree_pruned$Get("beta_A_f") %>% as_tibble()
Beta_sampleB_Females_tree_withTVB <- LR_tree_pruned$Get("beta_B_f") %>% as_tibble()
Beta_sampleA_Females_tree_noTBV <- LR_tree_pruned$Get("beta_A_f_noTBV") %>% as_tibble()
Beta_sampleB_Females_tree_noTBV <- LR_tree_pruned$Get("beta_B_f_noTBV") %>% as_tibble()
```

## Transpose 

### Beta values that control for TBV at leaves & tree
```{r}
Beta_sampleA_Females_withTVB_transpose <- as.data.frame(t(as.matrix(Beta_sampleA_Females_withTVB)))
Beta_sampleB_Females_withTVB_transpose <- as.data.frame(t(as.matrix(Beta_sampleB_Females_withTVB)))
Beta_sampleA_Females_withTVB_tree_transpose <- as.data.frame(t(as.matrix(Beta_sampleA_Females_tree_withTVB)))
Beta_sampleB_Females_withTVB_tree_transpose <- as.data.frame(t(as.matrix(Beta_sampleB_Females_tree_withTVB)))
```

### Beta values that do NOT control for TBV at leaves & tree
```{r}
Beta_sampleA_Females_noTVB_transpose <- as.data.frame(t(as.matrix(Beta_sampleA_Females_noTBV)))
Beta_sampleB_Females_noTVB_transpose <- as.data.frame(t(as.matrix(Beta_sampleB_Females_noTBV)))
Beta_sampleA_Females_noTVB_tree_transpose <- as.data.frame(t(as.matrix(Beta_sampleA_Females_tree_noTBV)))
Beta_sampleB_Females_noTVB_tree_transpose <- as.data.frame(t(as.matrix(Beta_sampleB_Females_tree_noTBV)))
```



## Look at the mean and sd of the beta values calculated above
```{r}
LR_tree_pruned$Do(function(node){
  #for XXY males
  node$beta_A_f_mean <- mean(node$beta_A_f)
  node$beta_A_f_sd <- sd(node$beta_A_f)
  node$beta_A_f_noTBV_mean <- mean(node$beta_A_f_noTBV)
  node$beta_A_f_noTBV_sd <- sd(node$beta_A_f_noTBV)
  #for XYY males
  node$beta_B_f_mean <- mean(node$beta_B_f)
  node$beta_B_f_sd <- sd(node$beta_B_f)
  node$beta_B_f_noTBV_mean <- mean(node$beta_B_f_noTBV)
  node$beta_B_f_noTBV_sd <- sd(node$beta_B_f_noTBV)
})
```

## Store the mean and sd for the leaves for XXY 
```{r}
beta_means_wTBV_XXY <- LR_tree_pruned$Get("beta_A_f_mean", filterFun = isLeaf)
beta_sds_wTBV_XXY <- LR_tree_pruned$Get("beta_A_f_sd", filterFun = isLeaf)
beta_means_noTBV_XXY <- LR_tree_pruned$Get("beta_A_f_noTBV_mean", filterFun = isLeaf)
beta_sds_noTBV_XXY <- LR_tree_pruned$Get("beta_A_f_noTBV_sd", filterFun = isLeaf)
## store the mean and sd for the leaves for XYY 
beta_means_wTBV_XYY <- LR_tree_pruned$Get("beta_B_f_mean", filterFun = isLeaf)
beta_sds_wTBV_XYY <- LR_tree_pruned$Get("beta_B_f_sd", filterFun = isLeaf)
beta_means_noTBV_XYY <- LR_tree_pruned$Get("beta_B_f_noTBV_mean", filterFun = isLeaf)
beta_sds_noTBV_XYY <- LR_tree_pruned$Get("beta_B_f_noTBV_sd", filterFun = isLeaf)
```


# Correlating beta values

### Females with TBV correction, just leaves
Correlate effect sizes such that column 1 is correlated with column 2 etc...
```{r}
split.pair.cors.effs_females_tbv <- rep(0, 1000)
for(i in 1:1000) {
  split.pair.cors.effs_females_tbv[i] <- cor(Beta_sampleA_Females_withTVB_transpose[,i], Beta_sampleB_Females_withTVB_transpose[,i])}
summary(split.pair.cors.effs_females_tbv)
```

### Plot distribution of correlations
```{r}
split_corr_wTBV <-split.pair.cors.effs_females_tbv %>% as.data.frame()
vec1 <- rep(c("Split control corr"), 10000)
df_split_corr_wTBV <- cbind(vec1, split_corr_wTBV)
colnames(df_split_corr_wTBV)<- c("vec1", "correlation")

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Female_Split_Corr_distribution_leaves_wTBV.pdf",
     width = 5,
     height = 4)
ggplot(df_split_corr_wTBV, aes(x=correlation, fill="red")) +
    geom_density(alpha=.3) +
   scale_fill_manual(labels = NULL, name=NULL, values=c('red'))+
    theme_classic()+ xlab("Correlation coefficient")+ylab("Density")+
   theme(text = element_text(size = 14))+
    geom_vline(xintercept=c(0))
```

### Plot example beta coefficients
```{r}
summary(cor(Beta_sampleA_Females_withTVB_transpose[,35], Beta_sampleB_Females_withTVB_transpose[,35]))

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Female_Representative_beta_split_corr_wTBV_leaves.pdf",
     width = 5,
     height = 4)
sample_beta_wTBV_leaves<-as.data.frame(cbind(Beta_sampleA_Females_withTVB_transpose[,35], Beta_sampleB_Females_withTVB_transpose[,35]))
colnames(sample_beta_wTBV_leaves) <- c("XXY_sampleA", "XYY_sampleB")
ggplot(sample_beta_wTBV_leaves, aes(x=XXY_sampleA, y=XYY_sampleB)) + 
  geom_point(size=2, alpha=0.8) + geom_smooth(method=lm)  + geom_abline() + 
  theme_classic()+xlab("Beta XXY_M Female")+ ylab("Beta XYY_M Female")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))+ 
  xlim(-1.5,1.5) + ylim(-1.5,1.5)
```
#### Females with TBV correction whole tree
```{r}
split.pair.cors.effs_females_tree_tbv <- rep(0, 1000)
for(i in 1:1000) {
  split.pair.cors.effs_females_tree_tbv[i] <- cor(Beta_sampleA_Females_withTVB_tree_transpose[,i], Beta_sampleB_Females_withTVB_tree_transpose[,i])}
summary(split.pair.cors.effs_females_tree_tbv)
```
### Plot distribution of correlations
```{r}
split_corr_wTBV_tree <-split.pair.cors.effs_females_tree_tbv %>% as.data.frame()
vec1 <- rep(c("Split control corr"), 10000)
df_split_corr_wTBV_tree <- cbind(vec1, split_corr_wTBV_tree)
colnames(df_split_corr_wTBV_tree)<- c("vec1", "correlation")

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Female_Split_Corr_distribution_tree_WTBV.pdf",
     width = 5,
     height = 4)

ggplot(df_split_corr_wTBV_tree, aes(x=correlation, fill="red")) +
    geom_density(alpha=.3) +
   scale_fill_manual(labels = NULL, name=NULL, values=c('red'))+
    theme_classic()+ xlab("Correlation coefficient")+ylab("Density")+
   theme(text = element_text(size = 14))+
    geom_vline(xintercept=c(0))
```
### Plot example beta coefficients
```{r}
summary(cor(Beta_sampleA_Females_withTVB_tree_transpose[,35], Beta_sampleB_Females_withTVB_tree_transpose[,35]))

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Female_Representative_beta_split_corr_wTBV_tree_1.pdf",
     width = 5,
     height = 4)
sample_beta_wTBV_tree<-as.data.frame(cbind(Beta_sampleA_Females_withTVB_tree_transpose[,35], Beta_sampleB_Females_withTVB_tree_transpose[,35]))
colnames(sample_beta_wTBV_tree) <- c("XXY_samleA", "XYY_sampleB")
ggplot(sample_beta_wTBV_tree, aes(x=XXY_samleA, y=XYY_sampleB)) + 
  geom_point() + geom_smooth(method=lm)  + geom_abline() + 
  theme_classic()+xlab("Beta XXY_M Female")+ ylab("Beta XYY_M Female")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))+ 
  xlim(-1.5,1.5) + ylim(-1.5,1.5)
```



### Females without TBV correction, just leaves
```{r}
split.pair.cors.effs_females_notbv <- rep(0, 1000)
for(i in 1:1000) {
  split.pair.cors.effs_females_notbv[i] <- cor(Beta_sampleA_Females_noTVB_transpose[,i], Beta_sampleB_Females_noTVB_transpose[,i])}
summary(split.pair.cors.effs_females_notbv)
```

### Plot distribution of correlations
```{r}
split_corr_noTBV_leaves <-split.pair.cors.effs_females_notbv %>% as.data.frame()
vec1 <- rep(c("Split control corr"), 10000)
df_split_corr_noTBV_leaves <- cbind(vec1, split_corr_noTBV_leaves)
colnames(df_split_corr_noTBV_leaves)<- c("vec1", "correlation")

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Female_Split_Corr_distribution_leaves_noTBV.pdf",
     width = 5,
     height = 4)

ggplot(df_split_corr_noTBV_leaves, aes(x=correlation, fill="red")) +
    geom_density(alpha=.3) +
   scale_fill_manual(labels =NULL, name=NULL, values=c('red'))+
    theme_classic()+ xlab("Correlation coefficient")+ylab("Density")+
   theme(text = element_text(size = 14))+
    geom_vline(xintercept=c(0))
```
### Plot example beta coefficients
```{r}
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Female_Representative_beta_split_corr_noTBV_leaves.pdf",
     width = 5,
     height = 4)
summary(cor(Beta_sampleA_Females_noTVB_transpose[,35], Beta_sampleB_Females_noTVB_transpose[,35]))

sample_beta_noTBV_leaves<-as.data.frame(cbind(Beta_sampleA_Females_noTVB_transpose[,35], Beta_sampleB_Females_noTVB_transpose[,35]))
colnames(sample_beta_noTBV_leaves) <- c("XXY_sampleA", "XYY_sampleB")
ggplot(sample_beta_noTBV_leaves, aes(x=XXY_sampleA, y=XYY_sampleB)) + 
  geom_point() + geom_smooth(method=lm)  + geom_abline() + 
  theme_classic()+xlab("Beta XXY_M Female")+ ylab("Beta XYY_M Female")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))+ 
  xlim(-1.5,1.5) + ylim(-1.5,1.5)
```


#### Females without TBV correction, across whole tree
```{r}
split.pair.cors.effs_females_tree_notbv <- rep(0, 1000)
for(i in 1:1000) {
  split.pair.cors.effs_females_tree_notbv[i] <- cor(Beta_sampleA_Females_noTVB_tree_transpose[,i], Beta_sampleB_Females_noTVB_tree_transpose[,i])}
summary(split.pair.cors.effs_females_tree_notbv)
```

### Plot distribution of correlations
```{r}
split_corr_noTBV_tree <-split.pair.cors.effs_females_tree_notbv %>% as.data.frame()
vec1 <- rep(c("Split control corr"), 10000)
df_split_corr_noTBV_tree <- cbind(vec1, split_corr_noTBV_tree)
colnames(df_split_corr_noTBV_tree)<- c("vec1", "correlation")

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Females_Split_Corr_distribution_tree_noTBV.pdf",
     width = 5,
     height = 4)

ggplot(df_split_corr_noTBV_tree, aes(x=correlation, fill="red")) +
    geom_density(alpha=.3) +
   scale_fill_manual(labels = NULL, name=NULL, values=c('red'))+
    theme_classic()+ xlab("Correlation coefficient")+ylab("Density")+
   theme(text = element_text(size = 14))+
    geom_vline(xintercept=c(0))
```
### Plot example beta coefficients
```{r}
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Females_Representative_beta_split_corr_noTBV_tree.pdf",
     width = 5,
     height = 4)

summary(cor(Beta_sampleA_Females_noTVB_tree_transpose[,35], Beta_sampleB_Females_noTVB_tree_transpose[,35]))

sample_beta_noTBV_tree<-as.data.frame(cbind(Beta_sampleA_Females_noTVB_tree_transpose[,35], Beta_sampleB_Females_noTVB_tree_transpose[,35]))
colnames(sample_beta_noTBV_tree) <- c("XXY_sampleA", "XYY_sampleB")
ggplot(sample_beta_noTBV_tree, aes(x=XXY_sampleA, y=XYY_sampleB)) + 
  geom_point() + geom_smooth(method=lm)  + geom_abline() + 
  theme_classic()+xlab("Beta XXY_M Females")+ ylab("Beta XYY_M Females")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))+ 
  xlim(-1.5,1.5) + ylim(-1.5,1.5)
```




# Directionality of effects

Here we will investigate whether the added X or Y chromosomes have similar effects on brain anatomy and try to identify the regions that are either both increased or decreased due to the anueploidy, and that are consistent across split halves (i.e. both increased or decreased in 95 of the 100 splits) 

### First we will look at the leaves with TBV effects
```{r}
#Set up a matrix in which to store the directionality of effects
congruence.holder.withTBV <- data.frame(both.pos=rep(NA, dim(Beta_sampleA_Females_withTVB_transpose)[1]), both.neg=rep(NA, dim(Beta_sampleA_Females_withTVB_transpose)[1]))
#head(congruence.holder.withTBV)
rownames(congruence.holder.withTBV) <- rownames(Beta_sampleA_Females_withTVB_transpose)
```

### Loop over all regions and assign congruence
```{r}
for (i in 1:dim(Beta_sampleA_Females_withTVB_transpose)[1]) {
  bound.rows <- rbind(Beta_sampleA_Females_withTVB_transpose[i,], Beta_sampleB_Females_withTVB_transpose [i,])
  congruence <- apply(bound.rows, 2, function(x) sum(x>0))
  congruence.holder.withTBV$both.pos[i] <- sum(congruence==2)
  congruence.holder.withTBV$both.neg[i] <- sum(congruence==0)
}
```

### Arrange lists
```{r}
arrange(congruence.holder.withTBV, desc(both.neg)) %>% filter(both.neg>949)
arrange(congruence.holder.withTBV, desc(both.pos)) %>% filter(both.pos>949)
```
### Save outputs
```{r}
congruence.holder.withTBV <- as.tibble(congruence.holder.withTBV)
label_names <- LR_tree_pruned$Get("levelName", filterFun = isLeaf) %>% as.data.frame()
congruence_females_withTBV <-  cbind(label_names, congruence.holder.withTBV)
write.csv(congruence_females_withTBV, file="/Users/gumae2/Documents/Humouse/analysis/split-half-analysis-outputs/congruence_beta_withTBV_females_1000_nowm_LR_split.csv")
```

### Load in colour palette

```{r}
#MRIcrotome:::defaultCol() ## use to look at hidden function that are loaded in with MRIcrotome
#MRIcrotome:::defaultCol ## use to see specific code used to define the defaultCol used in the plotting
labelVol <- mincArray(mincGetVolume("/Users/gumae2/Documents/Humouse/input_data/DSURQE_40micron_labels.mnc"))
anatVol <- mincArray(mincGetVolume("/Users/gumae2/Documents/Humouse/input_data/DSURQE_40micron_average.mnc"))
labelCols <- hanatToVolume(treeVols_LR, labelVol, "color_hex_triplet") #load in the Allen atlas colours to display next to the results

positive_cols <- function() {
  getOption("MRIcrotomeCol", colorRampPalette(c("yellow","red","firebrick"))(255))
}

negative_cols <- function() {
  getOption("MRIcrotomeRcol", colorRampPalette(c("turquoise3","royalblue","navyblue"))(255))
}
```

### Merge congruence maps
```{r}
congruence_females_withTBV$label<-rownames(congruence_females_withTBV)
congruence_positive <- congruence_females_withTBV$both.pos > 949
congruence_positive_wTBV <-congruence_females_withTBV[congruence_positive,]
congruence_females_withTBV$both.neg.neg <- congruence_females_withTBV$both.neg*(-1)
congruence_negative <- congruence_females_withTBV$both.neg.neg< -949
congruence_negative_wTBV <-congruence_females_withTBV[congruence_negative,]
congruence_pos_neg_wTBV <- congruence_females_withTBV[congruence_positive | congruence_negative, ]
sig_beta_XYY_tree<-left_join(congruence_females_withTBV, congruence_pos_neg_wTBV, by = "label")

sig_beta_XYY_tree$congruence <- sig_beta_XYY_tree$both.pos.y + sig_beta_XYY_tree$both.neg.neg.y
```




## Next we will look at the leaves without TBV effects
```{r}
congruence.holder.noTBV <- data.frame(both.pos=rep(NA, dim(Beta_sampleA_Females_noTVB_transpose)[1]), both.neg=rep(NA, dim(Beta_sampleA_Females_noTVB_transpose)[1]))
#head(congruence.holder.noTBV)
rownames(congruence.holder.noTBV) <- rownames(Beta_sampleA_Females_noTVB_transpose)

#Loop over all regions and assign congruence

for (i in 1:dim(Beta_sampleA_Females_noTVB_transpose)[1]) {
  bound.rows <- rbind(Beta_sampleA_Females_noTVB_transpose[i,], Beta_sampleB_Females_noTVB_transpose [i,])
  congruence <- apply(bound.rows, 2, function(x) sum(x>0))
  congruence.holder.noTBV$both.pos[i] <- sum(congruence==2)
  congruence.holder.noTBV$both.neg[i] <- sum(congruence==0)
}

#Arrange lists
arrange(congruence.holder.noTBV, desc(both.neg)) %>% filter(both.neg>949)
arrange(congruence.holder.noTBV, desc(both.pos)) %>% filter(both.pos>949)

#Save Outputs
congruence.holder.noTBV <- as.tibble(congruence.holder.noTBV)
label_names <- LR_tree_pruned$Get("levelName", filterFun = isLeaf) %>% as.data.frame()
congruence_females_noTBV <-  cbind(label_names, congruence.holder.noTBV)
write.csv(congruence_females_noTBV, file="/Users/gumae2/Documents/Humouse/analysis/split-half-analysis-outputs/congruence_beta_noTBV_females1000_LRsplit.csv")
```

### Merge congruence maps
```{r}
congruence_females_noTBV$label<-rownames(congruence_females_noTBV)
congruence_positive <- congruence_females_noTBV$both.pos > 949
congruence_positive_noTBV <-congruence_females_noTBV[congruence_positive,]
congruence_females_noTBV$both.neg.neg <- congruence_females_noTBV$both.neg*(-1)
congruence_negative <- congruence_females_noTBV$both.neg.neg< -949
congruence_negative_noTBV <-congruence_females_noTBV[congruence_negative,]
congruence_pos_neg_noTBV <- congruence_females_noTBV[congruence_positive | congruence_negative, ]
sig_beta_XYY_tree_noTBV<-left_join(congruence_females_noTBV, congruence_pos_neg_noTBV, by = "label")

sig_beta_XYY_tree_noTBV$congruence <- sig_beta_XYY_tree_noTBV$both.pos.y + sig_beta_XYY_tree_noTBV$both.neg.neg.y
```




## Next we will look across the tree with TBV effects
```{r}
congruence.holder.tree.withTBV <- data.frame(both.pos=rep(NA, dim(Beta_sampleA_Females_withTVB_tree_transpose)[1]), both.neg=rep(NA, dim(Beta_sampleA_Females_withTVB_tree_transpose)[1]))
#head(congruence.holder.tree.withTBV)
rownames(congruence.holder.tree.withTBV) <- rownames(Beta_sampleA_Females_withTVB_tree_transpose)

#Loop over all regions and assign congruence

for (i in 1:dim(Beta_sampleA_Females_withTVB_tree_transpose)[1]) {
  bound.rows <- rbind(Beta_sampleA_Females_withTVB_tree_transpose[i,], Beta_sampleB_Females_withTVB_tree_transpose [i,])
  congruence <- apply(bound.rows, 2, function(x) sum(x>0))
  congruence.holder.tree.withTBV$both.pos[i] <- sum(congruence==2)
  congruence.holder.tree.withTBV$both.neg[i] <- sum(congruence==0)
}

#Arrange lists
arrange(congruence.holder.tree.withTBV, desc(both.neg)) %>% filter(both.neg>949)
arrange(congruence.holder.tree.withTBV, desc(both.pos)) %>% filter(both.pos>949)

#Save Outputs
congruence.holder.tree.withTBV <- as.tibble(congruence.holder.tree.withTBV)
label_names <- LR_tree_pruned$Get("levelName") %>% as.data.frame()
congruence_females_tree_withTBV <-  cbind(label_names, congruence.holder.tree.withTBV)
congruence_females_tree_withTBV$both.neg.neg <- congruence_females_tree_withTBV$both.neg*(-1)
write.csv(congruence_females_tree_withTBV, file="/Users/gumae2/Documents/Humouse/analysis/split-half-analysis-outputs/congruence_beta_wholetree_withTBV_females_1000_LRsplit.csv")
```

### Merge congruence maps
```{r}
congruence_females_tree_withTBV$label<-rownames(congruence_females_tree_withTBV)
congruence_positive <- congruence_females_tree_withTBV$both.pos > 949
congruence_positive_wTBV <-congruence_females_tree_withTBV[congruence_positive,]
congruence_females_tree_withTBV$both.neg.neg <- congruence_females_tree_withTBV$both.neg*(-1)
congruence_negative <- congruence_females_tree_withTBV$both.neg.neg< -949
congruence_negative_wTBV <-congruence_females_tree_withTBV[congruence_negative,]
congruence_pos_neg_wTBV <- congruence_females_tree_withTBV[congruence_positive | congruence_negative, ]
congruence_tree<-left_join(congruence_females_tree_withTBV, congruence_pos_neg_wTBV, by = "label")

congruence_tree$congruence <- congruence_tree$both.pos.y + congruence_tree$both.neg.neg.y
```

### Attach congruence values to tree for plotting
```{r}
LR_tree_pruned$Do(function(node){
  ind_cong <- which(congruence_tree$label == node$name)
  node$congruence <- congruence_tree$congruence[ind_cong]
  })
```

### Both positive and both negative congruence map
```{r}
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Female_Mouse_congruence_tree_wTBV_1000_nowm_LRsplit.pdf",   # The directory you want to save the file in
    width = 3.5, # The width of the plot in inches
    height = 6) # The height of the plot in inches

congruence_wTBV <- hanatToVolume(LR_tree_pruned, labelVol, "congruence") #convert congruence map into mincarray
sliceSeries(nrow=7, ncol=1, begin=70, end=342) %>% 
  anatomy(anatVol, low=700, high=1400) %>% overlay(labelCols, low=0, high=1) %>% addtitle("Atlas") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(congruence_wTBV, low=950, high=1000, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>%
  legend("Congruence (1000 splits)") %>% addtitle("Congruence") %>% draw()
```


## Finally, we will look across the tree without controlling for TBV effects
```{r}
congruence.holder.tree.noTBV <- data.frame(both.pos=rep(NA, dim(Beta_sampleA_Females_noTVB_tree_transpose)[1]), both.neg=rep(NA, dim(Beta_sampleA_Females_noTVB_tree_transpose)[1]))
#head(congruence.holder.tree.noTBV)
rownames(congruence.holder.tree.noTBV) <- rownames(Beta_sampleA_Females_noTVB_tree_transpose)

#Loop over all regions and assign congruence
for (i in 1:dim(Beta_sampleA_Females_noTVB_tree_transpose)[1]) {
  bound.rows <- rbind(Beta_sampleA_Females_noTVB_tree_transpose[i,], Beta_sampleB_Females_noTVB_tree_transpose [i,])
  congruence <- apply(bound.rows, 2, function(x) sum(x>0))
  congruence.holder.tree.noTBV$both.pos[i] <- sum(congruence==2)
  congruence.holder.tree.noTBV$both.neg[i] <- sum(congruence==0)
}

#Arrange lists
arrange(congruence.holder.tree.noTBV, desc(both.neg)) %>% filter(both.neg>949)
arrange(congruence.holder.tree.noTBV, desc(both.pos)) %>% filter(both.pos>949)

#Save Outputs
congruence.holder.tree.noTBV <- as.tibble(congruence.holder.tree.noTBV)
label_names <- LR_tree_pruned$Get("levelName") %>% as.data.frame()
congruence_females_tree_noTBV <-  cbind(label_names, congruence.holder.tree.noTBV)
write.csv(congruence_females_tree_noTBV, file="/Users/gumae2/Documents/Humouse/analysis/split-half-analysis-outputs/congruence_beta_wholetree_noTBV_females_1000.csv")
```

### Merge congruence maps
```{r}
congruence_females_tree_noTBV$label<-rownames(congruence_females_tree_noTBV)
congruence_positive <- congruence_females_tree_noTBV$both.pos > 949
congruence_positive_wTBV <-congruence_females_tree_noTBV[congruence_positive,]
congruence_females_tree_noTBV$both.neg.neg <- congruence_females_tree_noTBV$both.neg*(-1)
congruence_negative <- congruence_females_tree_noTBV$both.neg.neg< -949
congruence_negative_wTBV <-congruence_females_tree_noTBV[congruence_negative,]
congruence_pos_neg_wTBV <- congruence_females_tree_noTBV[congruence_positive | congruence_negative, ]
congruence_tree_noTBV<-left_join(congruence_females_tree_noTBV, congruence_pos_neg_wTBV, by = "label")

congruence_tree_noTBV$congruence <- congruence_tree_noTBV$both.pos.y + congruence_tree_noTBV$both.neg.neg.y
```

### Attach congruence values to tree for plotting
```{r}
LR_tree_pruned$Do(function(node){
  ind_cong <- which(congruence_tree_noTBV$label == node$name)
  node$congruence_noTBV <- congruence_tree_noTBV$congruence[ind_cong]
  })
```

### Both positive and both negative congruence map
```{r, fig.width=2.5,fig.height=3.5}
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Female_Mouse_congruence_tree_noTBV_1000_nowm.pdf",   # The directory you want to save the file in
    width = 3.2, # The width of the plot in inches
    height = 6) # The height of the plot in inches

congruence_noTBV <- hanatToVolume(LR_tree_pruned, labelVol, "congruence_noTBV") #convert congruence map into mincarray
sliceSeries(nrow=7, ncol=1, begin=62, end=342) %>%
  anatomy(anatVol, low=700, high=1400) %>% overlay(labelCols, low=0, high=1) %>% addtitle("Atlas") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(congruence_noTBV, low=950, high=1000, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>%
  legend("Congruence (1000 splits)") %>% addtitle("Congruence") %>% draw()
```
