---
title: "Mouse-split-half-LR-split"
author: "Elisa Guma"
date: "4/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r }
library(tidyverse)
library(data.tree)
library(RMINC)
library(magrittr)
library(ggplot2)
library(MRIcrotome)
```

#Description

Since each mouse aneuploidy group in our mouse sample did not have their own independent control (as it does in the human sample), we performed  bootstrap resampling without replacement to generate two independent control groups as follows: we repeatedly split (n=1000) the XY control group (n=18) in half, sample A (n=9) and sample B (n=9), without replacement. Sample A was used to calculate z-scored brain volumes for the XXY mice, while sample B was used for the XYY_M mice. For each control-split, and across all brain regions, a linear model to assess for group effects, with correction for total brain volume. For each control split, the β1 was stored.

Mouse model Sample A: ROI_volume ~ intercept + β1(Group XYY_M vs XY_SampleA)+ β2(Total Brain Volume) + Ɛ
Mouse model Sample B: ROI_volume ~ intercept + β1(Group XYY_M vs XY_SampleB)+ β2(Total Brain Volume) + Ɛ

The β1 value of each brain region for sample A was correlated to that of Sample B across every region in the brain, yielding a 1000 x 1000 correlation matrix for each of the control splits. Next, we identified which brain regions had either a consistently positive or a consistently negative β1 value across 95% of the splits (950/1000 splits) for both the XXY_M (with XY_M Sample A) and XYY_M (with XY_M Sample B) groups. Analysis were repeated without TTV correction. 

```{r}
pathHome <- "/Users/gumae2/Documents/Humouse/"
demographics <- readRDS(str_c(pathHome, "input_data/", "gf2018noout.RDS"))
treeVols_LR <- readRDS(str_c(pathHome, "input_data/", "SCT-vols-no-outliers.RDS"))

source('/Users/gumae2/Documents/Humouse/input_data/tree_tools.R')
```

# Gonadal Males
Calculate total tissue volume
```{r}
vols <- treeVols_LR$Get("volumes") %>% as_tibble
dat <- vols %>%  cbind(demographics)

demographics$shorthand <- recode_factor(demographics$shorthand, XYM = "XY_M", XXYM="XXY_M", XYYM="XYY_M")
demographics$ventricle_volume <- vols$`ventricular systems`
demographics$total_tissue_volume<- demographics$brainVolume - demographics$ventricle_volume
```

```{r}
LR_tree_pruned <- Clone(treeVols_LR)
nodes_to_cut <- c("ventricular systems", "fiber tracts") #remove ventricles and cranial nerves
pruneAnatTree(LR_tree_pruned, nodes = nodes_to_cut, method = "AtNode")
```

## Select the rows from the demographics dataset that correspond to the groups of interest
```{r}
rows_just_xy <- which(demographics$shorthand == "XY_M")
rows_XXY <- which(demographics$shorthand == "XXY_M")
rows_XYY <- which(demographics$shorthand == "XYY_M")
```
## Assign the number of samples
```{r}
nsamples <- 1000
```

### Sample indices for half of the rows corresponding to UY-Sry
```{r}
#set.seed(42)
listSampleIndices <- vector(mode = "list", length = nsamples)
for(i in 1:nsamples){
  listSampleIndices[[i]] = sample(x = 1:length(rows_just_xy), size = 0.5*length(rows_just_xy), replace = FALSE)
}
```

#### Next we compute the split-half zscores in the tree
```{r}
#This is done at each node
LR_tree_pruned$Do(function(node){
    #For the given node, iterate over our permutations
   #Attach metadata to the tree
    node$demographics <- demographics
    node$genotype <- demographics$genotype
    node$brainVolume <- demographics$brainVolume
    node$tissueVolume <- demographics$total_tissue_volume
    node$shorthand <- demographics$shorthand
    node$sex <- demographics$sex

   #initialize vectors in which to store the betas from linear model
    node$beta_A_m <- numeric(nsamples)
    node$beta_B_m <- numeric(nsamples)
    node$beta_A_m_noTBV <- numeric(nsamples)
    node$beta_B_m_noTBV <- numeric(nsamples)
    
   #initialize vectors in which to store the sigma-betas from linear model
    node$sigma_beta_A_m <- numeric(nsamples)
    node$sigma_beta_B_m <- numeric(nsamples)
    node$sigma_beta_A_m_noTBV <- numeric(nsamples)
    node$sigma_beta_B_m_noTBV <- numeric(nsamples)
  
  for(i in 1:nsamples){
    #Using the sampled indices, extract the sets of rows corresponding to XY entries    
    rows_xy_sampleA <- rows_just_xy[listSampleIndices[[i]]] #sample A are the rows that are selected in the listSampleIndices above
    rows_xy_sampleB <- rows_just_xy[-listSampleIndices[[i]]] #sample B are the remaining rows 

    rows_XXYM <- which(demographics$shorthand == "XXY_M") #select the XXY row (redundant from above)
    rows_XYYM <- which(demographics$shorthand == "XYY_M") #select the XYY rows 
    
    rows_sampleA<-c(rows_XXYM, rows_xy_sampleA)
    rows_sampleB<-c(rows_XYYM, rows_xy_sampleB)
 
    #Compute the zscores for all volumes and store them in the correct position in the node
    #calculate the mean for XY sample A for each volume in the node
    node$ctrl_mean_sampleA <- mean(node$volumes[rows_xy_sampleA]) 
    node$ctrl_sd_sampleA <- sd(node$volumes[rows_xy_sampleA]) #same for the sd
    node$zscores_sampleA <- (node$volumes - node$ctrl_mean_sampleA)/node$ctrl_sd_sampleA #zscore relative to XY sample A
   #repeat for sample B
    node$ctrl_mean_sampleB <- mean(node$volumes[rows_xy_sampleB])
    node$ctrl_sd_sampleB <- sd(node$volumes[rows_xy_sampleB])
    node$zscores_sampleB  <- (node$volumes - node$ctrl_mean_sampleB)/node$ctrl_sd_sampleB #zscore relative to XY sample B
   
   #calculate TBV
   #calculate the z-scored brain volume with the newly split controls
   node$mean_tissueVolume_sampleA <- mean(node$tissueVolume[rows_xy_sampleA])
   node$sd_tissueVolume_sampleA <- sd(node$tissueVolume[rows_xy_sampleA])
   node$zscored_tissueVolume_sampleA <- (node$tissueVolume - node$mean_tissueVolume_sampleA)/node$sd_tissueVolume_sampleA
   node$mean_tissueVolume_sampleB <- mean(node$tissueVolume[rows_xy_sampleB])
   node$sd_tissueVolume_sampleB <- sd(node$tissueVolume[rows_xy_sampleB])
   node$zscored_tissueVolume_sampleB <- (node$tissueVolume - node$mean_tissueVolume_sampleB)/node$sd_tissueVolume_sampleB
   #  # 
 
    #load in the computed z-scores
   node$model_df_A <- node$demographics %>% mutate(zscores_A = node$zscores_sampleA) %>% mutate(zscored_tissueVolume_A = node$zscored_tissueVolume_sampleA) %>% mutate(shorthand = factor(shorthand, levels = c("XY_M", "XXY_M")))
   node$model_df_B <- node$demographics %>% mutate(zscores_B = node$zscores_sampleB) %>% mutate(zscored_tissueVolume_B = node$zscored_tissueVolume_sampleB) %>% mutate(shorthand = factor(shorthand, levels = c("XY_M", "XYY_M")))

    #load in the computed z-scores
   node$model_df_A_noTBV <- node$model_df_A
   node$model_df_B_noTBV <- node$model_df_B

#subset the correct rows
  node$model_df_A <- node$model_df_A[rows_sampleA, ]
  node$model_df_B <- node$model_df_B[rows_sampleB, ]
  node$model_df_A_noTBV <- node$model_df_A_noTBV[rows_sampleA, ]
  node$model_df_B_noTBV <- node$model_df_B_noTBV[rows_sampleB, ]

#run the linear model
  node$model_A <- summary(lm(zscores_A ~ shorthand + zscored_tissueVolume_A, data = node$model_df_A))
  node$model_B <- summary(lm(zscores_B ~ shorthand + zscored_tissueVolume_B, data = node$model_df_B))
  node$beta_A_noTBV <- summary(lm(zscores_A ~ shorthand , data = node$model_df_A_noTBV))
  node$beta_B_noTBV <- summary(lm(zscores_B ~ shorthand , data = node$model_df_B_noTBV))
 
#store the beta coefficients
  node$beta_A_m[i] <- node$model_A$coefficients["shorthandXXY_M", "Estimate"]
  node$beta_B_m[i] <- node$model_B$coefficients["shorthandXYY_M", "Estimate"]
  node$beta_A_m_noTBV[i] <- node$beta_A_noTBV$coefficients["shorthandXXY_M", "Estimate"]
  node$beta_B_m_noTBV[i] <- node$beta_B_noTBV$coefficients["shorthandXYY_M", "Estimate"]
  
  node$sigma_beta_A_m[i] <- node$model_A$coefficients["shorthandXXY_M", "Std. Error"]
  node$sigma_beta_B_m[i] <- node$model_B$coefficients["shorthandXYY_M", "Std. Error"]
  node$sigma_beta_A_m_noTBV[i] <- node$beta_A_noTBV$coefficients["shorthandXXY_M", "Std. Error"]
  node$sigma_beta_B_m_noTBV[i] <- node$beta_B_noTBV$coefficients["shorthandXYY_M", "Std. Error"]
  }
})  
```


## Extract 

## Beta values for each linear model at the leaves for models with and without TBV correction
```{r}
Beta_sampleA_Males_withTVB <- LR_tree_pruned$Get("beta_A_m", filterFun = isLeaf) %>% as_tibble()
Beta_sampleB_Males_withTVB <- LR_tree_pruned$Get("beta_B_m", filterFun = isLeaf) %>% as_tibble()
Beta_sampleA_Males_noTBV <- LR_tree_pruned$Get("beta_A_m_noTBV", filterFun = isLeaf) %>% as_tibble()
Beta_sampleB_Males_noTBV <- LR_tree_pruned$Get("beta_B_m_noTBV", filterFun = isLeaf) %>% as_tibble()
```

### Beta values for each linear model across the whole tree with and without TBV correction
```{r}
Beta_sampleA_Males_tree_withTVB <- LR_tree_pruned$Get("beta_A_m") %>% as_tibble()
Beta_sampleB_Males_tree_withTVB <- LR_tree_pruned$Get("beta_B_m") %>% as_tibble()
Beta_sampleA_Males_tree_noTBV <- LR_tree_pruned$Get("beta_A_m_noTBV") %>% as_tibble()
Beta_sampleB_Males_tree_noTBV <- LR_tree_pruned$Get("beta_B_m_noTBV") %>% as_tibble()
```

## Transpose 

### Beta values that control for TBV at leaves & tree
```{r}
Beta_sampleA_Males_withTVB_transpose <- as.data.frame(t(as.matrix(Beta_sampleA_Males_withTVB)))
Beta_sampleB_Males_withTVB_transpose <- as.data.frame(t(as.matrix(Beta_sampleB_Males_withTVB)))
Beta_sampleA_Males_withTVB_tree_transpose <- as.data.frame(t(as.matrix(Beta_sampleA_Males_tree_withTVB)))
Beta_sampleB_Males_withTVB_tree_transpose <- as.data.frame(t(as.matrix(Beta_sampleB_Males_tree_withTVB)))
```

### Beta values that do NOT control for TBV at leaves & tree
```{r}
Beta_sampleA_Males_noTVB_transpose <- as.data.frame(t(as.matrix(Beta_sampleA_Males_noTBV)))
Beta_sampleB_Males_noTVB_transpose <- as.data.frame(t(as.matrix(Beta_sampleB_Males_noTBV)))
Beta_sampleA_Males_noTVB_tree_transpose <- as.data.frame(t(as.matrix(Beta_sampleA_Males_tree_noTBV)))
Beta_sampleB_Males_noTVB_tree_transpose <- as.data.frame(t(as.matrix(Beta_sampleB_Males_tree_noTBV)))
```


## Look at the mean and sd of the beta values calculated above
```{r}
LR_tree_pruned$Do(function(node){
  #for XXY males
  node$beta_A_m_mean <- mean(node$beta_A_m)
  node$beta_A_m_sd <- sd(node$beta_A_m)
  node$beta_A_m_noTBV_mean <- mean(node$beta_A_m_noTBV)
  node$beta_A_m_noTBV_sd <- sd(node$beta_A_m_noTBV)
  #for XYY males
  node$beta_B_m_mean <- mean(node$beta_B_m)
  node$beta_B_m_sd <- sd(node$beta_B_m)
  node$beta_B_m_noTBV_mean <- mean(node$beta_B_m_noTBV)
  node$beta_B_m_noTBV_sd <- sd(node$beta_B_m_noTBV)
})
```

## Store the mean and sd for the leaves for XXY 
```{r}
beta_means_wTBV_XXY <- LR_tree_pruned$Get("beta_A_m_mean", filterFun = isLeaf)
beta_sds_wTBV_XXY <- LR_tree_pruned$Get("beta_A_m_sd", filterFun = isLeaf)
beta_means_noTBV_XXY <- LR_tree_pruned$Get("beta_A_m_noTBV_mean", filterFun = isLeaf)
beta_sds_noTBV_XXY <- LR_tree_pruned$Get("beta_A_m_noTBV_sd", filterFun = isLeaf)
## store the mean and sd for the leaves for XYY 
beta_means_wTBV_XYY <- LR_tree_pruned$Get("beta_B_m_mean", filterFun = isLeaf)
beta_sds_wTBV_XYY <- LR_tree_pruned$Get("beta_B_m_sd", filterFun = isLeaf)
beta_means_noTBV_XYY <- LR_tree_pruned$Get("beta_B_m_noTBV_mean", filterFun = isLeaf)
beta_sds_noTBV_XYY <- LR_tree_pruned$Get("beta_B_m_noTBV_sd", filterFun = isLeaf)
```


# Correlating beta values

### Males with TBV correction, just leaves
Correlate effect sizes such that column 1 is correlated with column 2 etc...
```{r}
split_ctl_corr_males_tbv <- rep(0, 1000)
for(i in 1:1000) {
  split_ctl_corr_males_tbv[i] <- cor(Beta_sampleA_Males_withTVB_transpose[ ,i],Beta_sampleB_Males_withTVB_transpose[,i])}
summary(split_ctl_corr_males_tbv)
```

### Plot distribution of correlations
```{r}
split_corr_wTBV <-split_ctl_corr_males_tbv %>% as.data.frame()
vec1 <- rep(c("Split control corr"), 10000)
df_split_corr_wTBV <- cbind(vec1, split_corr_wTBV)
colnames(df_split_corr_wTBV)<- c("vec1", "correlation")

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Mouse_Split_Corr_distribution_leaves_wTBV.pdf",
     width = 5,
     height = 4)
ggplot(df_split_corr_wTBV, aes(x=correlation, fill="red")) +
    geom_density(alpha=.3) +
   scale_fill_manual(labels = NULL, name=NULL, values=c('red'))+
    theme_classic()+ xlab("Correlation coefficient")+ylab("Density")+
   theme(text = element_text(size = 14))+
    geom_vline(xintercept=c(0))
```

### Plot example beta coefficients
```{r}
summary(cor(Beta_sampleA_Males_withTVB_transpose[,35], Beta_sampleB_Males_withTVB_transpose[,35]))

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Representative_beta_split_corr_wTBV_leaves.pdf",
     width = 5,
     height = 4)
sample_beta_wTBV_leaves<-as.data.frame(cbind(Beta_sampleA_Males_withTVB_transpose[,34], Beta_sampleB_Males_withTVB_transpose[,34]))
colnames(sample_beta_wTBV_leaves) <- c("XXY_sampleA", "XYY_sampleB")
ggplot(sample_beta_wTBV_leaves, aes(x=XXY_sampleA, y=XYY_sampleB)) + 
  geom_point(size=2, alpha=0.8) + geom_smooth(method=lm)  + geom_abline() + 
  theme_classic()+xlab("Beta XXY_M")+ ylab("Beta XYY_M")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))+ 
  xlim(-1.5,1.5) + ylim(-1.5,1.5)
```

#### Males with TBV correction whole tree
```{r}
split.pair.cors.effs_males_tree_tbv <- rep(0, 1000)
for(i in 1:1000) {
  split.pair.cors.effs_males_tree_tbv[i] <- cor(Beta_sampleA_Males_withTVB_tree_transpose[,i], Beta_sampleB_Males_withTVB_tree_transpose[,i])}
summary(split.pair.cors.effs_males_tree_tbv)
```
### Plot distribution of correlations
```{r}
split_corr_wTBV_tree <-split.pair.cors.effs_males_tree_tbv %>% as.data.frame()
vec1 <- rep(c("Split control corr"), 10000)
df_split_corr_wTBV_tree <- cbind(vec1, split_corr_wTBV_tree)
colnames(df_split_corr_wTBV_tree)<- c("vec1", "correlation")

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Mouse_Split_Corr_distribution_tree_WTBV.pdf",
     width = 5,
     height = 4)

ggplot(df_split_corr_wTBV_tree, aes(x=correlation, fill="red")) +
    geom_density(alpha=.3) +
   scale_fill_manual(labels = NULL, name=NULL, values=c('red'))+
    theme_classic()+ xlab("Correlation coefficient")+ylab("Density")+
   theme(text = element_text(size = 14))+
    geom_vline(xintercept=c(0))
```
### Plot example beta coefficients
```{r}
summary(cor(Beta_sampleA_Males_withTVB_tree_transpose[,35], Beta_sampleB_Males_withTVB_tree_transpose[,35]))

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Representative_beta_split_corr_wTBV_tree_1.pdf",
     width = 5,
     height = 4)
sample_beta_wTBV_tree<-as.data.frame(cbind(Beta_sampleA_Males_withTVB_tree_transpose[,35], Beta_sampleB_Males_withTVB_tree_transpose[,35]))
colnames(sample_beta_wTBV_tree) <- c("XXY_samleA", "XYY_sampleB")
ggplot(sample_beta_wTBV_tree, aes(x=XXY_samleA, y=XYY_sampleB)) + 
  geom_point() + geom_smooth(method=lm)  + geom_abline() + 
  theme_classic()+xlab("Beta XXY_M")+ ylab("Beta XYY_M")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))+ 
  xlim(-1.5,1.5) + ylim(-1.5,1.5)
```


### Males without TBV correction, just leaves
```{r}
split.pair.cors.effs_males_notbv <- rep(0, 1000)
for(i in 1:1000) {
  split.pair.cors.effs_males_notbv[i] <- cor(Beta_sampleA_Males_noTVB_transpose[,i], Beta_sampleB_Males_noTVB_transpose[,i])}
summary(split.pair.cors.effs_males_notbv)
```

### Plot distribution of correlations
```{r}
split_corr_noTBV_leaves <-split.pair.cors.effs_males_notbv %>% as.data.frame()
vec1 <- rep(c("Split control corr"), 10000)
df_split_corr_noTBV_leaves <- cbind(vec1, split_corr_noTBV_leaves)
colnames(df_split_corr_noTBV_leaves)<- c("vec1", "correlation")

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Mouse_Split_Corr_distribution_leaves_noTBV.pdf",
     width = 5,
     height = 4)

ggplot(df_split_corr_noTBV_leaves, aes(x=correlation, fill="red")) +
    geom_density(alpha=.3) +
   scale_fill_manual(labels =NULL, name=NULL, values=c('red'))+
    theme_classic()+ xlab("Correlation coefficient")+ylab("Density")+
   theme(text = element_text(size = 14))+
    geom_vline(xintercept=c(0))
```
### Plot example beta coefficients
```{r}
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Representative_beta_split_corr_noTBV_leaves.pdf",
     width = 5,
     height = 4)
summary(cor(Beta_sampleA_Males_noTVB_transpose[,35], Beta_sampleB_Males_noTVB_transpose[,35]))

sample_beta_noTBV_leaves<-as.data.frame(cbind(Beta_sampleA_Males_noTVB_transpose[,35], Beta_sampleB_Males_noTVB_transpose[,35]))
colnames(sample_beta_noTBV_leaves) <- c("XXY_sampleA", "XYY_sampleB")
ggplot(sample_beta_noTBV_leaves, aes(x=XXY_sampleA, y=XYY_sampleB)) + 
  geom_point() + geom_smooth(method=lm)  + geom_abline() + 
  theme_classic()+xlab("Beta XXY_M")+ ylab("Beta XYY_M")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))+ 
  xlim(-1.5,1.5) + ylim(-1.5,1.5)
```


#### Males without TBV correction, across whole tree
```{r}
split.pair.cors.effs_males_tree_notbv <- rep(0, 1000)
for(j in 1:1000) {
  split.pair.cors.effs_males_tree_notbv[i] <- cor(Beta_sampleA_Males_noTVB_tree_transpose[,j], Beta_sampleB_Males_noTVB_tree_transpose[,j])}
summary(split.pair.cors.effs_males_tree_notbv)
```

### Plot distribution of correlations
```{r}
split_corr_noTBV_tree <-split.pair.cors.effs_males_tree_notbv %>% as.data.frame()
vec1 <- rep(c("Split control corr"), 10000)
df_split_corr_noTBV_tree <- cbind(vec1, split_corr_noTBV_tree)
colnames(df_split_corr_noTBV_tree)<- c("vec1", "correlation")

pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Mouse_Split_Corr_distribution_tree_noTBV.pdf",
     width = 5,
     height = 4)

ggplot(df_split_corr_noTBV_tree, aes(x=correlation, fill="red")) +
    geom_density(alpha=.3) +
   scale_fill_manual(labels = NULL, name=NULL, values=c('red'))+
    theme_classic()+ xlab("Correlation coefficient")+ylab("Density")+
   theme(text = element_text(size = 14))+
    geom_vline(xintercept=c(0))
```
### Plot example beta coefficients
```{r}
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Representative_beta_split_corr_noTBV_tree.pdf",
     width = 5,
     height = 4)

summary(cor(Beta_sampleA_Males_noTVB_tree_transpose[,35], Beta_sampleB_Males_noTVB_tree_transpose[,35]))

sample_beta_noTBV_tree<-as.data.frame(cbind(Beta_sampleA_Males_noTVB_tree_transpose[,35], Beta_sampleB_Males_noTVB_tree_transpose[,35]))
colnames(sample_beta_noTBV_tree) <- c("XXY_sampleA", "XYY_sampleB")
ggplot(sample_beta_noTBV_tree, aes(x=XXY_sampleA, y=XYY_sampleB)) + 
  geom_point() + geom_smooth(method=lm)  + geom_abline() + 
  theme_classic()+xlab("Beta XXY_M")+ ylab("Beta XYY_M")+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14))+ 
  xlim(-1.5,1.5) + ylim(-1.5,1.5)
```


# Directionality of effects

Here we will investigate whether the added X or Y chromosomes have similar effects on brain anatomy and try to identify the regions that are either both increased or decreased due to the anueploidy, and that are consistent across split halves (i.e. both increased or decreased in 95 of the 100 splits) 

### First we will look at the leaves with TBV effects
```{r}
#Set up a matrix in which to store the directionality of effects
congruence.holder.withTBV <- data.frame(both.pos=rep(NA, dim(Beta_sampleA_Males_withTVB_transpose)[1]), both.neg=rep(NA, dim(Beta_sampleA_Males_withTVB_transpose)[1]))
rownames(congruence.holder.withTBV) <- rownames(Beta_sampleA_Males_withTVB_transpose)
```

### Loop over all regions and assign congruence
Here we are looping through each beta value for the 1000 splits, and determining which rows are either both positive in the XXY and XYY groups, or both negative in the two groups. With this information, we can then sum the number of times (across the 1000 splits) that a region is positive or negative in both groups. This way, we can identify regions that are consistenlty congruently increased or decreased across groups and splits (as a measure of reliability)
```{r}
for (i in 1:dim(Beta_sampleA_Males_withTVB_transpose)[1]) {
  bound.rows <- rbind(Beta_sampleA_Males_withTVB_transpose[i,], Beta_sampleB_Males_withTVB_transpose [i,])
  congruence <- apply(bound.rows, 2, function(x) sum(x>0))
  congruence.holder.withTBV$both.pos[i] <- sum(congruence==2)
  congruence.holder.withTBV$both.neg[i] <- sum(congruence==0)
}
```

### Arrange lists
```{r}
arrange(congruence.holder.withTBV, desc(both.neg)) %>% filter(both.neg>949)
arrange(congruence.holder.withTBV, desc(both.pos)) %>% filter(both.pos>949)
```

### Save outputs
```{r}
congruence.holder.withTBV <- as.tibble(congruence.holder.withTBV)
label_names <- LR_tree_pruned$Get("levelName", filterFun = isLeaf) %>% as.data.frame()
congruence_males_withTBV <-  cbind(label_names, congruence.holder.withTBV)
write.csv(congruence_males_withTBV, file="/Users/gumae2/Documents/Humouse/analysis/split-half-analysis-outputs/congruence_beta_withTBV_males_1000_nowm_LR_split.csv")
```

### Load in colour palette

```{r}
labelVol <- mincArray(mincGetVolume("/Users/gumae2/Documents/Humouse/input_data/DSURQE_40micron_labels.mnc"))
anatVol <- mincArray(mincGetVolume("/Users/gumae2/Documents/Humouse/input_data/DSURQE_40micron_average.mnc"))
labelCols <- hanatToVolume(treeVols_LR, labelVol, "color_hex_triplet") #load in the Allen atlas colours to display next to the results

positive_cols <- function() {
  getOption("MRIcrotomeCol", colorRampPalette(c("yellow","red","firebrick"))(255))
}

negative_cols <- function() {
  getOption("MRIcrotomeRcol", colorRampPalette(c("turquoise3","royalblue","navyblue"))(255))
}
```

### Merge congruence maps
```{r}
congruence_males_withTBV$label<-rownames(congruence_males_withTBV)
congruence_positive <- congruence_males_withTBV$both.pos > 949
congruence_positive_wTBV <-congruence_males_withTBV[congruence_positive,]
congruence_males_withTBV$both.neg.neg <- congruence_males_withTBV$both.neg*(-1)
congruence_negative <- congruence_males_withTBV$both.neg.neg< -949
congruence_negative_wTBV <-congruence_males_withTBV[congruence_negative,]
congruence_pos_neg_wTBV <- congruence_males_withTBV[congruence_positive | congruence_negative, ]
sig_beta_XYY_tree<-left_join(congruence_males_withTBV, congruence_pos_neg_wTBV, by = "label")

sig_beta_XYY_tree$congruence <- sig_beta_XYY_tree$both.pos.y + sig_beta_XYY_tree$both.neg.neg.y
```

## Next we will look at the leaves without TBV effects
```{r}
congruence.holder.noTBV <- data.frame(both.pos=rep(NA, dim(Beta_sampleA_Males_noTVB_transpose)[1]), both.neg=rep(NA, dim(Beta_sampleA_Males_noTVB_transpose)[1]))
rownames(congruence.holder.noTBV) <- rownames(Beta_sampleA_Males_noTVB_transpose)

#Loop over all regions and assign congruence

for (i in 1:dim(Beta_sampleA_Males_noTVB_transpose)[1]) {
  bound.rows <- rbind(Beta_sampleA_Males_noTVB_transpose[i,], Beta_sampleB_Males_noTVB_transpose [i,])
  congruence <- apply(bound.rows, 2, function(x) sum(x>0))
  congruence.holder.noTBV$both.pos[i] <- sum(congruence==2)
  congruence.holder.noTBV$both.neg[i] <- sum(congruence==0)
}

#Arrange lists
arrange(congruence.holder.noTBV, desc(both.neg)) %>% filter(both.neg>950)
arrange(congruence.holder.noTBV, desc(both.pos)) %>% filter(both.pos>950)

#Save Outputs
congruence.holder.noTBV <- as.tibble(congruence.holder.noTBV)
label_names <- LR_tree_pruned$Get("levelName", filterFun = isLeaf) %>% as.data.frame()
congruence_males_noTBV <-  cbind(label_names, congruence.holder.noTBV)
write.csv(congruence_males_noTBV, file="/Users/gumae2/Documents/Humouse/analysis/split-half-analysis-outputs/congruence_beta_noTBV_males1000_LRsplit.csv")
```

### Merge congruence maps
```{r}
congruence_males_noTBV$label<-rownames(congruence_males_noTBV)
congruence_positive <- congruence_males_noTBV$both.pos > 949
congruence_positive_noTBV <-congruence_males_noTBV[congruence_positive,]
congruence_males_noTBV$both.neg.neg <- congruence_males_noTBV$both.neg*(-1)
congruence_negative <- congruence_males_noTBV$both.neg.neg< -949
congruence_negative_noTBV <-congruence_males_noTBV[congruence_negative,]
congruence_pos_neg_noTBV <- congruence_males_noTBV[congruence_positive | congruence_negative, ]
sig_beta_XYY_tree_noTBV<-left_join(congruence_males_noTBV, congruence_pos_neg_noTBV, by = "label")

sig_beta_XYY_tree_noTBV$congruence <- sig_beta_XYY_tree_noTBV$both.pos.y + sig_beta_XYY_tree_noTBV$both.neg.neg.y
```


## Next we will look across the tree with TBV effects
```{r}
congruence.holder.tree.withTBV <- data.frame(both.pos=rep(NA, dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]), both.neg=rep(NA, dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]))
#head(congruence.holder.tree.withTBV)
rownames(congruence.holder.tree.withTBV) <- rownames(Beta_sampleA_Males_withTVB_tree_transpose)

#Loop over all regions and assign congruence

for (i in 1:dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]) {
  bound.rows <- rbind(Beta_sampleA_Males_withTVB_tree_transpose[i,], Beta_sampleB_Males_withTVB_tree_transpose [i,])
  congruence <- apply(bound.rows, 2, function(x) sum(x>0))
  congruence.holder.tree.withTBV$both.pos[i] <- sum(congruence==2)
  congruence.holder.tree.withTBV$both.neg[i] <- sum(congruence==0)
}

#Arrange lists
arrange(congruence.holder.tree.withTBV, desc(both.neg)) %>% filter(both.neg>949)
arrange(congruence.holder.tree.withTBV, desc(both.pos)) %>% filter(both.pos>949)

#Save Outputs
congruence.holder.tree.withTBV <- as.tibble(congruence.holder.tree.withTBV)
label_names <- LR_tree_pruned$Get("levelName") %>% as.data.frame()
congruence_males_tree_withTBV <-  cbind(label_names, congruence.holder.tree.withTBV)
congruence_males_tree_withTBV$both.neg.neg <- congruence_males_tree_withTBV$both.neg*(-1)
write.csv(congruence_males_tree_withTBV, file="/Users/gumae2/Documents/Humouse/analysis/split-half-analysis-outputs/congruence_beta_wholetree_withTBV_males_1000_LRsplit.csv")
```

### Merge congruence maps
This way we can plot the regions that are both positive or both negative in one brain map. To do so, we will convert the values for the congruently negative regions to be negative, so that they take on negative colours (blue)

```{r}
congruence_males_tree_withTBV$label<-rownames(congruence_males_tree_withTBV)
congruence_positive <- congruence_males_tree_withTBV$both.pos > 949
congruence_positive_wTBV <-congruence_males_tree_withTBV[congruence_positive,]
congruence_males_tree_withTBV$both.neg.neg <- congruence_males_tree_withTBV$both.neg*(-1)
congruence_negative <- congruence_males_tree_withTBV$both.neg.neg< -949
congruence_negative_wTBV <-congruence_males_tree_withTBV[congruence_negative,]
congruence_pos_neg_wTBV <- congruence_males_tree_withTBV[congruence_positive | congruence_negative, ]
congruence_tree<-left_join(congruence_males_tree_withTBV, congruence_pos_neg_wTBV, by = "label")

congruence_tree$congruence <- congruence_tree$both.pos.y + congruence_tree$both.neg.neg.y
```

### Attach congruence values to tree for plotting
```{r}
LR_tree_pruned$Do(function(node){
  ind_cong <- which(congruence_tree$label == node$name)
  node$congruence <- congruence_tree$congruence[ind_cong]
  })

#congruence_test <- tree$Get("congruence") %>% as_tibble()
```

### Both positive and both negative congruence map
```{r}
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Mouse_congruence_tree_wTBV_1000_nowm_LRsplit_1.pdf",   # The directory you want to save the file in
    width = 3.5, # The width of the plot in inches
    height = 6) # The height of the plot in inches

congruence_wTBV <- hanatToVolume(LR_tree_pruned, labelVol, "congruence") #convert congruence map into mincarray
sliceSeries(nrow=7, ncol=1, begin=70, end=342) %>% 
  anatomy(anatVol, low=700, high=1400) %>% overlay(labelCols, low=0, high=1) %>% addtitle("Atlas") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(congruence_wTBV, low=950, high=1000, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>%
  legend("Congruence (1000 splits)") %>% addtitle("Congruence") %>% draw()
```


## Finally, we will look across the tree without controlling for TBV effects
```{r}
congruence.holder.tree.noTBV <- data.frame(both.pos=rep(NA, dim(Beta_sampleA_Males_noTVB_tree_transpose)[1]), both.neg=rep(NA, dim(Beta_sampleA_Males_noTVB_tree_transpose)[1]))
#head(congruence.holder.tree.noTBV)
rownames(congruence.holder.tree.noTBV) <- rownames(Beta_sampleA_Males_noTVB_tree_transpose)

#Loop over all regions and assign congruence
for (i in 1:dim(Beta_sampleA_Males_noTVB_tree_transpose)[1]) {
  bound.rows <- rbind(Beta_sampleA_Males_noTVB_tree_transpose[i,], Beta_sampleB_Males_noTVB_tree_transpose [i,])
  congruence <- apply(bound.rows, 2, function(x) sum(x>0))
  congruence.holder.tree.noTBV$both.pos[i] <- sum(congruence==2)
  congruence.holder.tree.noTBV$both.neg[i] <- sum(congruence==0)
}

#Arrange lists
arrange(congruence.holder.tree.noTBV, desc(both.neg)) %>% filter(both.neg>949)
arrange(congruence.holder.tree.noTBV, desc(both.pos)) %>% filter(both.pos>949)

#Save Outputs
congruence.holder.tree.noTBV <- as.tibble(congruence.holder.tree.noTBV)
label_names <- LR_tree_pruned$Get("levelName") %>% as.data.frame()
congruence_males_tree_noTBV <-  cbind(label_names, congruence.holder.tree.noTBV)
write.csv(congruence_males_tree_noTBV, file="/Users/gumae2/Documents/Humouse/analysis/split-half-analysis-outputs/congruence_beta_wholetree_noTBV_males1000.csv")
```

### Merge congruence maps
```{r}
congruence_males_tree_noTBV$label<-rownames(congruence_males_tree_noTBV)
congruence_positive <- congruence_males_tree_noTBV$both.pos > 949
congruence_positive_wTBV <-congruence_males_tree_noTBV[congruence_positive,]
congruence_males_tree_noTBV$both.neg.neg <- congruence_males_tree_noTBV$both.neg*(-1)
congruence_negative <- congruence_males_tree_noTBV$both.neg.neg< -949
congruence_negative_wTBV <-congruence_males_tree_noTBV[congruence_negative,]
congruence_pos_neg_wTBV <- congruence_males_tree_noTBV[congruence_positive | congruence_negative, ]
congruence_tree_noTBV<-left_join(congruence_males_tree_withTBV, congruence_pos_neg_wTBV, by = "label")

congruence_tree_noTBV$congruence <- congruence_tree_noTBV$both.pos.y + congruence_tree_noTBV$both.neg.neg.y
```

### Attach congruence values to tree for plotting
```{r}
LR_tree_pruned$Do(function(node){
  ind_cong <- which(congruence_tree_noTBV$label == node$name)
  node$congruence_noTBV <- congruence_tree_noTBV$congruence[ind_cong]
  })

#congruence_test <- tree$Get("congruence") %>% as_tibble()
```

### Both positive and both negative congruence map
```{r, fig.width=2.5,fig.height=3.5}
pdf(file = "/Users/gumae2/Documents/Humouse_paper/Figures/mouse_unilateral/Mouse_congruence_tree_noTBV_1000_nowm.pdf",   # The directory you want to save the file in
    width = 3.2, # The width of the plot in inches
    height = 6) # The height of the plot in inches

congruence_noTBV <- hanatToVolume(LR_tree_pruned, labelVol, "congruence_noTBV") #convert congruence map into mincarray
sliceSeries(nrow=7, ncol=1, begin=62, end=342) %>%
  anatomy(anatVol, low=700, high=1400) %>% overlay(labelCols, low=0, high=1) %>% addtitle("Atlas") %>% 
  sliceSeries() %>% anatomy() %>%
  overlay(congruence_noTBV, low=950, high=1000, col = positive_cols(), rCol=negative_cols(), symmetric = T) %>%
  legend("Congruence (1000 splits)") %>% addtitle("Congruence") %>% draw()
```


# Identifying positive and negative beta values  for all samples

Next we will look at the sign per group for XXY (sample A) and XYY(sample B) with TBV as a covariate, and without, only at the leaves
```{r}
sign.holder.leaves <- data.frame(pos.XXY=rep(NA, dim(Beta_sampleA_Males_withTVB_transpose)[1]), neg.XXY=rep(NA, dim(Beta_sampleA_Males_withTVB_transpose)[1]), pos.XYY=rep(NA, dim(Beta_sampleA_Males_withTVB_transpose)[1]), neg.XYY=rep(NA, dim(Beta_sampleA_Males_withTVB_transpose)[1]), pos.noTBV.XXY=rep(NA, dim(Beta_sampleA_Males_withTVB_transpose)[1]), neg.noTBV.XXY=rep(NA, dim(Beta_sampleA_Males_withTVB_transpose)[1]), pos.noTBV.XYY=rep(NA, dim(Beta_sampleA_Males_withTVB_transpose)[1]), neg.noTBV.XYY=rep(NA, dim(Beta_sampleA_Males_withTVB_transpose)[1]))
#head(sign.holder.leaves)
rownames(sign.holder.leaves) <- rownames(Beta_sampleA_Males_withTVB_transpose)

#Loop over all regions and assign congruence
for (i in 1:dim(Beta_sampleA_Males_withTVB_transpose)[1]) {
  #With TBV as covariate (leaves)
  sign.pos.XXY <- apply(Beta_sampleA_Males_withTVB_transpose[i,], 2, function(x) x>0)
  sign.neg.XXY <- apply(Beta_sampleA_Males_withTVB_transpose[i,], 2, function(x) x<0)
  sign.pos.XYY <- apply(Beta_sampleB_Males_withTVB_transpose[i,], 2, function(x) x>0)
  sign.neg.XYY <- apply(Beta_sampleB_Males_withTVB_transpose[i,], 2, function(x) x<0)
  #Without TBV as covariate (leaves)
  sign.pos.noTBV.XXY <- apply(Beta_sampleA_Males_noTVB_transpose[i,], 2, function(x) x>0)
  sign.neg.noTBV.XXY <- apply(Beta_sampleA_Males_noTVB_transpose[i,], 2, function(x) x<0)
  sign.pos.noTBV.XYY <- apply(Beta_sampleB_Males_noTVB_transpose[i,], 2, function(x) x>0)
  sign.neg.noTBV.XYY <- apply(Beta_sampleB_Males_noTVB_transpose[i,], 2, function(x) x<0)

  ##how many times it's positive (over the 100 splits)
  #With TBV as covariate (leaves)
  sign.holder.leaves$pos.XXY[i] <- sum(sign.pos.XXY>0)
  sign.holder.leaves$neg.XXY[i] <- sum(sign.neg.XXY>0)
  sign.holder.leaves$pos.XYY[i] <- sum(sign.pos.XYY>0)
  sign.holder.leaves$neg.XYY[i] <- sum(sign.neg.XYY>0)
 #Without TBV as covariate (leaves)
  sign.holder.leaves$pos.noTBV.XXY[i] <- sum(sign.pos.noTBV.XXY>0)
  sign.holder.leaves$neg.noTBV.XXY[i] <- sum(sign.neg.noTBV.XXY>0)
  sign.holder.leaves$pos.noTBV.XYY[i] <- sum(sign.pos.noTBV.XYY>0)
  sign.holder.leaves$neg.noTBV.XYY[i] <- sum(sign.neg.noTBV.XYY>0)
}

#Arrange lists with TBV as covariate
arrange(sign.holder.leaves, desc(pos.XXY)) %>% filter(pos.XXY>950)
arrange(sign.holder.leaves, desc(neg.XXY)) %>% filter(neg.XXY>950)
arrange(sign.holder.leaves, desc(pos.XYY)) %>% filter(pos.XYY>950)
arrange(sign.holder.leaves, desc(neg.XYY)) %>% filter(neg.XYY>950)
#Arrange lists without TBV as covariate
arrange(sign.holder.leaves, desc(pos.noTBV.XXY)) %>% filter(pos.noTBV.XXY>950)
arrange(sign.holder.leaves, desc(neg.noTBV.XXY)) %>% filter(neg.noTBV.XXY>950)
arrange(sign.holder.leaves, desc(pos.noTBV.XYY)) %>% filter(pos.noTBV.XYY>950)
arrange(sign.holder.leaves, desc(neg.noTBV.XYY)) %>% filter(neg.noTBV.XYY>950)

#Save Outputs
sign.holder.leaves <- as.tibble(sign.holder.leaves)
label_names <- LR_tree_pruned$Get("levelName", filterFun = isLeaf) %>% as.data.frame()
males.sign.holder.leaves <-  cbind(label_names, sign.holder.leaves)

write.csv(males.sign.holder.leaves, file="/Users/gumae2/Documents/Humouse/analysis/split-half-analysis-outputs/signs_beta_males_leaves_LRsplit.csv")
```

### Identify ROIs that are both positive in XXY and negative in XYY 95% of the time

```{r}
posXXY_negXYY <- (males.sign.holder.leaves$pos.XXY > 949) | (males.sign.holder.leaves$neg.XYY >949)
posXXY_and_negXYY<- males.sign.holder.leaves$pos.XXY > 949 & males.sign.holder.leaves$neg.XYY >949
posXXY_and_negXYY_list <-males.sign.holder.leaves[posXXY_and_negXYY,]
posXXY_and_negXYY_list

posXYY_and_negXXY<- males.sign.holder.leaves$pos.XYY > 949 & males.sign.holder.leaves$neg.XXY >949 
posXYY_and_negXXY_list <-males.sign.holder.leaves[posXYY_and_negXXY,]
posXYY_and_negXXY_list
```

Next we will look at the sign per group for XXY (sample A) and XYY(sample B) with TBV as a covariate, and without, across the whole tree
```{r}
sign.holder.tree <- data.frame(pos.XXY=rep(NA, dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]), neg.XXY=rep(NA, dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]), pos.XYY=rep(NA, dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]), neg.XYY=rep(NA, dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]), pos.noTBV.XXY=rep(NA, dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]), neg.noTBV.XXY=rep(NA, dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]), pos.noTBV.XYY=rep(NA, dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]), neg.noTBV.XYY=rep(NA, dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]))
#head(sign.holder.tree)
rownames(sign.holder.tree) <- rownames(Beta_sampleA_Males_withTVB_tree_transpose)

#Loop over all regions and assign congruence
for (i in 1:dim(Beta_sampleA_Males_withTVB_tree_transpose)[1]) {
  #With TBV as covariate (leaves)
  sign.pos.XXY <- apply(Beta_sampleA_Males_withTVB_tree_transpose[i,], 2, function(x) x>0)
  sign.neg.XXY <- apply(Beta_sampleA_Males_withTVB_tree_transpose[i,], 2, function(x) x<0)
  sign.pos.XYY <- apply(Beta_sampleB_Males_withTVB_tree_transpose[i,], 2, function(x) x>0)
  sign.neg.XYY <- apply(Beta_sampleB_Males_withTVB_tree_transpose[i,], 2, function(x) x<0)
  #Without TBV as covariate (leaves)
  sign.pos.noTBV.XXY <- apply(Beta_sampleA_Males_noTVB_tree_transpose[i,], 2, function(x) x>0)
  sign.neg.noTBV.XXY <- apply(Beta_sampleA_Males_noTVB_tree_transpose[i,], 2, function(x) x<0)
  sign.pos.noTBV.XYY <- apply(Beta_sampleB_Males_noTVB_tree_transpose[i,], 2, function(x) x>0)
  sign.neg.noTBV.XYY <- apply(Beta_sampleB_Males_noTVB_tree_transpose[i,], 2, function(x) x<0)

  ##how many times it's positive (over the 100 splits)
  #With TBV as covariate (leaves)
  sign.holder.tree$pos.XXY[i] <- sum(sign.pos.XXY>0)
  sign.holder.tree$neg.XXY[i] <- sum(sign.neg.XXY>0)
  sign.holder.tree$pos.XYY[i] <- sum(sign.pos.XYY>0)
  sign.holder.tree$neg.XYY[i] <- sum(sign.neg.XYY>0)
 #Without TBV as covariate (leaves)
  sign.holder.tree$pos.noTBV.XXY[i] <- sum(sign.pos.noTBV.XXY>0)
  sign.holder.tree$neg.noTBV.XXY[i] <- sum(sign.neg.noTBV.XXY>0)
  sign.holder.tree$pos.noTBV.XYY[i] <- sum(sign.pos.noTBV.XYY>0)
  sign.holder.tree$neg.noTBV.XYY[i] <- sum(sign.neg.noTBV.XYY>0)
}

#Arrange lists with TBV as covariate
arrange(sign.holder.tree, desc(pos.XXY)) %>% filter(pos.XXY>950)
arrange(sign.holder.tree, desc(neg.XXY)) %>% filter(neg.XXY>950)
arrange(sign.holder.tree, desc(pos.XYY)) %>% filter(pos.XYY>950)
arrange(sign.holder.tree, desc(neg.XYY)) %>% filter(neg.XYY>950)

#Arrange lists without TBV as covariate
arrange(sign.holder.tree, desc(pos.noTBV.XXY)) %>% filter(pos.noTBV.XXY>950)
arrange(sign.holder.tree, desc(neg.noTBV.XXY)) %>% filter(neg.noTBV.XXY>950)
arrange(sign.holder.tree, desc(pos.noTBV.XYY)) %>% filter(pos.noTBV.XYY>950)
arrange(sign.holder.tree, desc(neg.noTBV.XYY)) %>% filter(neg.noTBV.XYY>950)

#Save Outputs
sign.holder.tree <- as.tibble(sign.holder.tree)
label_names_tree <- LR_tree_pruned$Get("levelName") %>% as.data.frame()
males.sign.holder.tree <-  cbind(label_names_tree, sign.holder.tree)
write.csv(males.sign.holder.tree, file="/Users/gumae2/Documents/Humouse/analysis/split-half-analysis-outputs/signs_beta_males_tree_1000_LRsplit.csv")

```

### Identify ROIs that are both positive in XXY and negative in XYY 95% of the time

```{r}
posXXY_negXYY <- (sign.holder.tree$pos.XXY > 949) | (sign.holder.tree$neg.XYY >949)
posXXY_and_negXYY<- sign.holder.tree$pos.XXY > 949 & sign.holder.tree$neg.XYY >949
posXXY_and_negXYY_list <-sign.holder.tree[posXXY_and_negXYY,]
posXXY_and_negXYY_list

posXYY_and_negXXY<- sign.holder.tree$pos.XYY > 949 & sign.holder.tree$neg.XXY >949 
posXYY_and_negXXY_list <-sign.holder.tree[posXYY_and_negXXY,]
posXYY_and_negXXY_list
```